---
title: "ER2_with dynamic dosing_modified"
author: "Xuefen Yin"
date: "2024-11-6"
output: pdf_document
---

# R setup
```{r setup, echo = F}

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

rm(list=ls(all=TRUE))

library(tidyverse)
library(mrgsolve)
library(ggplot2)
library(survival)
library(survminer)
library(gridExtra)
library(muhaz)
library(zoo)
library(ggExtra)
library(patchwork)
library(ggridges)
library(purrr)
library(grid)
library(cowplot)
library(openxlsx)
library(brms) ## Emax
library(broom)
library(readxl)

new_path <- paste("C:/rtools44/usr/bin", "C:/rtools44/mingw64/bin", Sys.getenv("PATH"), sep=";")
Sys.setenv(PATH = new_path)

theme_set(theme_bw())
```
#1 Common functions(run one time)

##1.1 common function for data visualization 

```{r}
custom_log_labels <- function(x) {
  ifelse(x < 10, 
         sprintf("%.1f", x),  # One decimal place for numbers < 10
         sprintf("%.0f", x))  # No decimal places for numbers >= 10
}

custom_theme <- theme_classic() +
  theme(
    panel.grid.major = element_line(color = "gray70", linewidth = 0.5),  # Major grid lines
    panel.grid.minor = element_line(color = "gray90", linewidth = 0.25)  # Minor grid lines
  )

# General KM plot function
KM_plot_G <- function(km_object, data, title_prefix, group_labels, colors, plot_x_scale = 600, save_path) {

    if (length(group_labels) != length(colors)) {
    stop("The length of group_labels and colors must be the same")
  }
  
  plot <- ggsurvplot(
    km_object,
    data = data,
    surv.median.line = "hv",
    conf.int = TRUE,
    #pval = TRUE,
    #pval.method = TRUE,
    risk.table = TRUE,
    risk.table.y.text = FALSE,
    tables.theme = theme_cleantable(),
    tables.height = 0.25,
    palette = colors,
    legend.labs = group_labels,
    xlim = c(0, plot_x_scale),
    legend.title = element_blank() 
  ) + labs(
    y = "Probability of No Event",
    x = "Days",
    title = paste("True ER relationship -", title_prefix)
  )

  plot$plot <- plot$plot +
    theme(plot.subtitle = element_text(size = 10)) +
    scale_x_continuous(breaks = seq(0, plot_x_scale, by = 50))
  
  
  if (identical(data, analysis)) {
    ggsave(filename = save_path, plot = plot$plot, width = 7, height = 5, dpi = 400, units = "in")
  }
    
  return(plot)
}


# KM plot function containing saving function
KM_plot_Q <- function(km_object, data, title_prefix,group_labels, colors,plot_x_scale = 600, save_path) {
  plot <- ggsurvplot(
    km_object,
    data = data,
    surv.median.line = "hv",
    conf.int = TRUE,
    #pval = TRUE,
   # pval.method = TRUE,
    risk.table = TRUE,
    risk.table.y.text = FALSE,
    tables.theme = theme_cleantable(),
    tables.height = 0.25,
    palette = colors,
    legend.labs = group_labels,
    xlim = c(0, plot_x_scale),
    legend.title = element_blank() 
  )+ labs( y = "Probability of No Event",
           x = "Days",
          title = paste("True ER relationship -",title_prefix)) 

   plot$plot <- plot$plot +
   theme(plot.subtitle = element_text(size = 10))+
   scale_x_continuous(breaks = seq(0, plot_x_scale, by = 50))
   
  # # Save the plot
   ggsave(filename = save_path, plot = plot$plot, width = 7, height = 5, dpi = 400, units = "in")
  
  return(plot)
}

###KM plot with no strata

KM_plot <- function(km_object, data, title_prefix,plot_x_scale = 600, save_path) {
    plot <- ggsurvplot(
    km_object,
    data = data,
    surv.median.line = "hv",
    color = "black",
    conf.int.fill = "grey45",
    conf.int = TRUE,
    title = paste("True ER -",title_prefix),
    xlab = "Days",
    ylab = "Probability of no event",
    xlim = c(0, plot_x_scale),
    risk.table = "abs_pct",
    risk.table.y.text = FALSE,
    cumcensor = TRUE,
    tables.theme = theme_cleantable(),
    tables.height = 0.15,
    legend = "none"
  )
  
  plot$plot <- plot$plot +
    theme(
      plot.title = element_text(size = 14),
      plot.subtitle = element_text(size = 12),
      axis.title = element_text(size = 14),
      axis.text = element_text(size = 12)
    ) +
    scale_x_continuous(breaks = seq(0, plot_x_scale, by = 50)) +
    theme(
      plot.title = element_text(hjust = 0.5),
     # axis.text.x = element_text(angle = 60)
    )
  
  # # Save the plot
   ggsave(filename = save_path, plot = plot$plot, width = 5, height = 4, dpi = 400, units = "in")
   
  return(plot)
}


# comparing tumor size change with the dose change
Tumor_Dose_plot <- function(id, data, response_duration, pfs_linear) {
  data <- data %>%
    filter(ID == id) 
  first_day <- response_duration$First_Response_Day[response_duration$ID == id]
  last_day <- response_duration$Last_Response_Day[response_duration$ID == id]
  pfs_day <- pfs_linear$DAY[pfs_linear$ID == id]
  
  max_tumor <- max(data$Tumor, na.rm = TRUE)
  max_dose <- max(data$DOSE, na.rm = TRUE)
  
  p <- ggplot(data, aes(x = DAY)) +
    geom_point(aes(y = DOSE / max_dose * max_tumor), color = "springgreen4", size = 1) +
    geom_line(aes(y = Tumor), size = 1.5, color = "black") +
    geom_line(aes(y = TumorB * 1.2), linetype = "dashed", color = "red", size = 0.5) +
    geom_line(aes(y = TumorB * 0.7), linetype = "dashed", color = "navyblue", size = 0.5) +
    theme_classic() +
    geom_vline(xintercept = first_day, color = "navyblue") +
    annotate("text", x = first_day, y = max_tumor * 0.75, label = as.character(first_day), vjust = 1.2, hjust = 0, size = 3, angle = 0, color = "navyblue", fontface = "bold") +
    geom_vline(xintercept = last_day, color = "navyblue") +
    annotate("text", x = last_day, y = max_tumor, label = as.character(last_day), vjust = 1.2, hjust = 0, size = 3, angle = 0, color = "navyblue", fontface = "bold") +
    geom_vline(xintercept = pfs_day, color = "red") +
    annotate("text", x = pfs_day, y = max_tumor * 0.75, label = as.character(pfs_day), vjust = 1.2, hjust = 0, size = 3, angle = 0, color = "red", fontface = "bold") +
    labs(
      x = "Time (Days)",
      y = "Tumor size (mm)",
      title = paste("ID-", id)
    ) +
    scale_y_continuous(
      name = "Tumor size (mm)",
      sec.axis = sec_axis(~ . * max_dose  / max_tumor, name = "Dose (mg)", 
                          breaks = seq(0, max_dose , by = 20)),
      limits = c(0, NA)
    ) +
    theme(
      panel.background = element_rect(fill = "white", color = "black"),
      panel.grid.major.y = element_line(color = "grey"),
      panel.grid.minor.x = element_line(color = "grey", linetype = 2),
      panel.grid.major.x = element_line(color = "grey"),
      legend.background = element_rect(fill = "transparent"),
      axis.text.x = element_text(size = 8, angle = 0),
      axis.text.y = element_text(size = 8),
      plot.title = element_text(hjust = 0.5)
    )
  
  return(p)
}

# comparing tumor size change with the exposure metrics change
PKPD_profile_plot <- function(id, data, response_duration, pfs_linear) {
  data <- data %>% filter(ID == id) 
  first_day <- response_duration$First_Response_Day[response_duration$ID == id]
  last_day <- response_duration$Last_Response_Day[response_duration$ID == id]
  pfs_day <- pfs_linear$DAY[pfs_linear$ID == id]
  
  max_tumor <- max(data$Tumor, na.rm = TRUE)
  max_CP <- max(data$CP, na.rm = TRUE)
  min_CP <- min(data$CP[data$CP > 0], na.rm = TRUE)  # Minimum non-zero CP value
  
  p <- ggplot(data, aes(x = DAY)) +
    geom_point(aes(y = scales::rescale(log10(CP), to = c(0, max_tumor))), color = "springgreen4", size = 1) +
    geom_line(aes(y = Tumor), size = 1.5, color = "black") +
    geom_line(aes(y = TumorB * 1.2), linetype = "dashed", color = "red", size = 0.5) +
    geom_line(aes(y = TumorB * 0.7), linetype = "dashed", color = "navyblue", size = 0.5) +
    theme_classic() +
    geom_vline(xintercept = first_day, color = "navyblue") +
    annotate("text", x = first_day, y = max_tumor * 0.75, label = as.character(first_day), vjust = 1.2, hjust = 0, size = 3, angle = 0, color = "navyblue", fontface = "bold") +
    geom_vline(xintercept = last_day, color = "navyblue") +
    annotate("text", x = last_day, y = max_tumor, label = as.character(last_day), vjust = 1.2, hjust = 0, size = 3, angle = 0, color = "navyblue", fontface = "bold") +
    geom_vline(xintercept = pfs_day, color = "red") +
    annotate("text", x = pfs_day, y = max_tumor * 0.75, label = as.character(pfs_day), vjust = 1.2, hjust = 0, size = 3, angle = 0, color = "red", fontface = "bold") +
    labs(
      x = "Time (Days)",
      y = "Tumor size (mm)",
      title = paste("ID-", id)
    ) +
    scale_y_continuous(
      name = "Tumor size (mm)",
      sec.axis = sec_axis(
        ~ 10^(. * (log10(max_CP) - log10(min_CP)) / max_tumor + log10(min_CP)),
        name = "Plasma concentration (ng/ml)",
        breaks = scales::trans_breaks("log10", function(x) 10^x),
        labels = scales::trans_format("log10", scales::math_format(10^.x))
      ),
      limits = c(0, NA)
    ) +
    theme(
      panel.background = element_rect(fill = "white", color = "black"),
      panel.grid.major.y = element_line(color = "grey"),
      panel.grid.minor.x = element_line(color = "grey", linetype = 2),
      panel.grid.major.x = element_line(color = "grey"),
      legend.background = element_rect(fill = "transparent"),
      axis.text.x = element_text(size = 8, angle = 0),
      axis.text.y = element_text(size = 8),
      plot.title = element_text(hjust = 0.5)
    )
  
  return(p)
}

# plot time-exposure metrics profile
Typical_plot_DH2 <- function(data, y_var, title) {
  ggplot(data, aes(x = DAY, y = !!sym(y_var), color = as.factor(ID))) +
    geom_point() +
    geom_line() +
    theme_classic() +
    theme(
      panel.background = element_rect(fill = "white"),
      panel.grid.major.y = element_line(color = "grey"),
      panel.grid.minor.x = element_line(color = "grey", linetype = 2),
      panel.grid.major.x = element_line(color = "grey"),
      legend.background = element_rect(fill = "transparent"),
      plot.title = element_text(hjust = 0.5),
      legend.key.size = unit(0.5, "lines"), # Reduce the legend key size
      legend.text = element_text(size = 6) # Reduce the legend text size
    ) +
    scale_color_brewer(palette = "Paired") +
    labs(x = "Time (days)",
         y = y_var,
         title = title,
         color = "ID")
}

# genetate plot of PK using ID having the median Ctrough at the end of first doing interval
CP_plot <- function(data, title) {
  ggplot(data, aes(x = time, y = CP, color = as.factor(ID))) +
    geom_point() +
    geom_line() +
    scale_y_log10() +
    theme_classic() +
    theme(
      panel.background = element_rect(fill = "white"),
      panel.grid.major.y = element_line(color = "grey"),
      panel.grid.minor.x = element_line(color = "grey", linetype = 2),
      panel.grid.major.x = element_line(color = "grey"),
      legend.background = element_rect(fill = "transparent"),
      plot.title = element_text(hjust = 0.5)
    ) +
    scale_color_brewer(palette = "Paired") +
    labs(x = "Time (hours)", y = "Concentration", title = title, color = "ID")
}


logistic_regression_PK <- function(summary_data, combined_data, df.ER.IDQ, x_var, y_var) {
  # Ensure x variable is numeric for log scale
  combined_data[[x_var]] <- as.numeric(combined_data[[x_var]])
  
  ggplot() +
  
       # True ER Logistic regression line
    geom_smooth(data = combined_data, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER Logistic Regression"), 
                method = "glm", method.args = list(family = "binomial")) +
    geom_point(data = combined_data, aes(x = .data[[x_var]], y = .data[[y_var]]), 
               shape = "|", alpha = 0.5) +
   
     # Logistic regression line for current dataset
    geom_smooth(data = df.ER.IDQ, aes(x = .data[[x_var]], y = .data[[y_var]], color = "Logistic Regression"), 
                method = "glm", method.args = list(family = "binomial")) +
    geom_point(data = df.ER.IDQ, aes(x = .data[[x_var]], y = .data[[y_var]]), 
               shape = "|", alpha = 0.5) +
    
    # Original True ER line
    geom_line(data = summary_data, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER"), size = 1.5) +
    geom_point(data = summary_data, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER"), size = 2) +
    geom_text(data = summary_data, aes(x = .data[[x_var]], y = .data[[y_var]], label = DOSE), 
              vjust = 0.2, hjust = -0.4,angle = 75, size = 3.5) +
    
    custom_theme +
    theme(
      panel.background = element_rect(fill = "white", color = "black"),
      legend.background = element_rect(fill = "transparent"),
      legend.position = c(0.3, 0.8),
      legend.title = element_blank(),
      axis.text.x = element_text(size = 12, angle = 0, hjust = 1),
      axis.text.y = element_text(size = 12),
      axis.title = element_text(size = 12),
      plot.title = element_text(size = 14, hjust = 0.5),
      plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm")
        ) +
    labs(
      x = x_var,
      y = "Probability of ORR Event",
      title = paste("Logistic Regression -", x_var),
      color = "Model"
    ) +
    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
    scale_x_log10(labels = custom_log_labels,limits = c(0.01, NA)) +
    scale_color_manual(values = c("True ER Logistic Regression" = "blue", "Logistic Regression" = "black", "True ER" = "forestgreen"))
}

logistic_regression_PD <- function(data, predictor, response) {
  # Ensure predictor is numeric for log scale
  data[[predictor]] <- as.numeric(data[[predictor]])

  plot <- data %>%
    ggplot(aes_string(x = predictor, y = response)) +
    geom_point(shape = "|") +
    geom_smooth(method = "glm", method.args = list(family = "binomial")) +
    scale_x_log10() +
    labs(x = predictor,
         y = "Probability of ORR Event",
         title = paste("Logistic Regression -", predictor))

  return(plot)
}


```

##1.2 common function to handle the dataset
```{r}
## split the dataset into 4 groups
quantiles <- function(data, column_name, labels = c("1", "2", "3", "4")) {
  quantiles <- quantile(data[[column_name]], probs = c(0.25, 0.5, 0.75))
  categorized_column <- cut(data[[column_name]],
                            breaks = c(-Inf, quantiles, Inf),
                            labels = labels,
                            include.lowest = TRUE)
  return(categorized_column)

}

## split the dataset into 3 groups
tertile <- function(data, column_name, labels = c("1", "2", "3")) {
  # Calculate the tertiles
  tertiles <- quantile(data[[column_name]], probs = c(1/3, 2/3))
  
  # Categorize the column based on the tertiles
  categorized_column <- cut(data[[column_name]], 
                            breaks = c(-Inf, tertiles, Inf), 
                            labels = labels, 
                            include.lowest = TRUE)
  return(categorized_column)
}

### perfrom the Mann-Whitney U-Test and save the result

wilcox <- function(df_group1, df_group2, variables) {
  # Initialize an empty data frame to store results
  results_df <- data.frame(p_value = numeric(), stringsAsFactors = FALSE)
  
  for (var in variables) {
    # Run the Wilcoxon test for the current variable
    test_result <- wilcox.test(df_group1[[var]], df_group2[[var]], paired = FALSE, alternative = "two.sided",
                               conf.int = TRUE, conf.level=0.95) # Note: corrected "confi.level" to "conf.level"
    
    # Append the variable name and p-value to the results dataframe
     temp_result <- data.frame(P.Value = test_result$p.value, stringsAsFactors = FALSE)
     rownames(temp_result) <- var
     
     results_df <- rbind(results_df, temp_result)
  }
  return(results_df)
}

### extract results from univariate Cox PH models_continuous

univ_con <- function(univ_models) {
    univ_results <- lapply(univ_models, function(x) {
    x <- summary(x)  # Summarize the model
    # Extract and format the results
    P.value <- signif(x$wald["pvalue"], digits=3)
    wald.test <- signif(x$wald["test"], digits=3)
    beta <- signif(x$coef[1], digits=3)  # Coefficient beta
    HR <- signif(exp(x$coef[1]), digits=3)  # Hazard Ratio (HR)
    HR.confint.lower <- signif(x$conf.int[,"lower .95"], 3)
    HR.confint.upper <- signif(x$conf.int[,"upper .95"], 3)
    HR <- paste0(HR, " (",
                 HR.confint.lower, "-", HR.confint.upper, ")")
    res <- c(beta, HR, wald.test, P.value)
    names(res) <- c("beta", "HR (95% CI for HR)", "wald.test", "P.Value")
    return(res)
  })
  # Convert the list of results to a dataframe
  result_df <- t(as.data.frame(univ_results))
  return(result_df)
}

### extract results from univariate Cox PH models_categorical_4 GROUP
univ_cat <- function(univ_models_G) {
  
          univ_results_G <- lapply(univ_models_G, function(x) { 
          x <- summary(x)

          # Extract Wald test p-value and statistic
          P.value<-signif(x$wald["pvalue"], digits=2)
          wald.test<-signif(x$wald["test"], digits=2)
          beta <- numeric(length = 3)
          HR <- numeric(length = 3)
          HR.confint.lower <- numeric(length = 3)
          HR.confint.upper <- numeric(length = 3)
          HRs <- character(length = 3)
  
          for (i in 1:3) {
            beta[i] <- signif(x$coef[i], digits = 3)
            HR[i] <- signif(exp(x$coef[i]), digits = 3) # HR
            HR.confint.lower[i] <- signif(x$conf.int[i,3],3)
            HR.confint.upper[i] <- signif(x$conf.int[i,4],3)
            HRs[i] <- paste0(HR[i], " (", HR.confint.lower[i], "-", HR.confint.upper[i], ")")
            }
           res <- c(beta, HRs, wald.test, P.value )
           names(res) <- c(paste0("Beta", 1:3), paste0("HR (95% CI) ", 1:3), "Wald.Test", "P.Value")
   
           return(res)

          })
          # Convert the list of results to a dataframe
          result_df <- t(as.data.frame(univ_results_G))
          return(result_df)
}  

## extract results from univariate Cox PH models_categorical_3 GROUP

univ_cat_T <- function(univ_models_G) {
  
          univ_results_G <- lapply(univ_models_G, function(x) { 
          x <- summary(x)

          # Extract Wald test p-value and statistic
          P.value<-signif(x$wald["pvalue"], digits=2)
          wald.test<-signif(x$wald["test"], digits=2)
          beta <- numeric(length = 2)
          HR <- numeric(length = 2)
          HR.confint.lower <- numeric(length = 2)
          HR.confint.upper <- numeric(length = 2)
          HRs <- character(length = 2)
  
          for (i in 1:2) {
            beta[i] <- signif(x$coef[i], digits = 3)
            HR[i] <- signif(exp(x$coef[i]), digits = 3) # HR
            HR.confint.lower[i] <- signif(x$conf.int[i,3],3)
            HR.confint.upper[i] <- signif(x$conf.int[i,4],3)
            HRs[i] <- paste0(HR[i], " (", HR.confint.lower[i], "-", HR.confint.upper[i], ")")
            }
           res <- c(beta, HRs, wald.test, P.value )
           names(res) <- c(paste0("Beta", 1:2), paste0("HR (95% CI) ", 1:2), "Wald.Test", "P.Value")
   
           return(res)

          })
          # Convert the list of results to a dataframe
          result_df <- t(as.data.frame(univ_results_G))
          return(result_df)
}  

# uni <- coxph(Surv(DAY, EVENT) ~ CtroughQ, data = df.ER)
# summary<- summary(uni)
# summary$conf.int

# extract results from univariate Cox PH models_continuous

logistic_analysis <- function(logistic_Results, covariates) {
  logistic_summaries <- lapply(logistic_Results, summary)
  
  logistic.results <- lapply(seq_along(logistic_summaries), function(i) {
    x <- logistic_summaries[[i]]
    P.value <- signif(x$coefficients[2, 4], digits=3)
    Slope <- signif(x$coefficients[2, 1], digits=3)
    AIC <- round(AIC(logistic_Results[[i]]), 1)   # Use the actual model object, not the summary
    res <- c(Slope, AIC, P.value)
    names(res) <- c("Slope","AIC", "P.Value")
    return(res)
  })
  
  # Convert the list of results to a dataframe
  result_df <- as.data.frame(do.call(rbind, logistic.results))
  row.names(result_df) <- covariates  # Add row names
  
  return(result_df)
}

Calculate_EC50_linear <- function(predictor, data) {
  
  # Initialize an empty list to store results
  EC50_results <- list()
  
  # Loop through each predictor in the predictor vector
  for (pred in predictor) {
    
    # Fit the logistic regression model
    formula <- as.formula(paste("EVENT ~", pred))
    model <- glm(formula, family="binomial", data=data)
    
    # Extract coefficients
    b0 <- coef(model)[1]
    b1 <- coef(model)[2]
    
    # Calculate EC50 and its standard error
    EC50 <- -b0 / b1
    dEC50_b0 <- -1 / b1
    dEC50_b1 <- b0 / b1^2
    dEC50_b <- matrix(c(dEC50_b0, dEC50_b1), ncol=1)
    V_EC50 <- t(dEC50_b) %*% vcov(model) %*% dEC50_b
    Std_Err <- sqrt(V_EC50)
    
    # Calculate confidence intervals
    LB <- EC50 - 1.96 * Std_Err
    UB <- EC50 + 1.96 * Std_Err
    
    # Store the results in the list
    EC50_results[[pred]] <- c(b0, b1, EC50, Std_Err, LB, UB)
  }
  
  # Convert the list to a matrix and set row and column names
  EC50_out <- do.call(rbind, EC50_results)
  colnames(EC50_out) <- c("b0", "b1", "EC50", "Std Err", "LB", "UB")
  rownames(EC50_out) <- predictor
  
  # Return the rounded results
  return(round(EC50_out, 4))
}
```

#2 Tumor growth profiles with treatment effect

-event=1, the event onset time will be the true event onset time(actual last assessment day without considering clinical visit situation). e.g., if the onset time is 17 days, then the time is 17 days;
-event=0, either the last observed event onset day (based on the overall ORR distribution after outlier removal) or the patient's actual last assessment day—whichever occurs earlier.

##2.1 using log transformed exposure metrics without using prediction funciton
```{r}
df.exp <- readRDS("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/PFS/True inverse ER_PFS_DH2_HL24_ID20871_ii24_60&40&20_LDR/df_exp.rds")
First_day_conc <- df.exp %>% filter(DAY==1)%>% select(ID, Ctrough, Cavg)%>% rename(Ctrough1D=Ctrough, Cavg1D=Cavg)

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/True ER relationship/DH1")
Modified_trueER_DH1 <- read.csv("True ER_ORR.csv")
Modified_trueER_DH1$avgDoseTE <- Modified_trueER_DH1$DOSE

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/True ER relationship/DH2_LDR")
Modified_trueER_DH2 <- read.csv("True ER_ORR_LDR_DH2.csv")

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/ORR_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_60&40&20_LDR")
df.ER.IDQ <- read.csv("df_ER_IDQ.csv")
ORR_responder <- df.ER.IDQ %>% filter(EVENT==1)

# Calculate Q1, Q3, and IQR for DAY
Q1 <- quantile(ORR_responder$DAY, 0.25)
Q3 <- quantile(ORR_responder$DAY, 0.75)
IQR <- Q3 - Q1

# Define outliers as points below Q1 - 1.5*IQR or above Q3 + 1.5*IQR
lower_bound <- Q1 - 1.5 * IQR
upper_bound <- Q3 + 1.5 * IQR

# Identify outliers
outliers <- ORR_responder %>% filter(DAY < lower_bound | DAY > upper_bound)
outliers_ID <- outliers %>%pull(ID)
Modified_onset <- ORR_responder %>% filter(!ID %in% outliers_ID) %>% slice_max(DAY, n = 1)
Onset_day <- unique(Modified_onset$DAY)

Analysis.PFS <-  df.exp %>%
        mutate( EVENT = if_else(Tumor < 1.2 * TumorB, 0, 1),
                LAST=0) %>%
        group_by(ID) %>%
         # Identify the first DAY where EVENT = 1 for each ID
         mutate(first_event_day = ifelse(EVENT == 1, DAY, NA_real_)) %>%
         mutate(first_event_day = min(first_event_day, na.rm = TRUE)) %>%
         # Keep all rows where EVENT = 0 or it's the first occurrence of EVENT = 1
         filter((EVENT == 0 & DAY < first_event_day) | (EVENT == 1 & DAY == first_event_day)) %>%
         mutate(last_day = max(DAY))%>%
         mutate(LAST = if_else(DAY == last_day | EVENT == 1, 1, LAST)) %>%
         ungroup()%>%
         select(-first_event_day,-last_day)%>% filter(LAST == 1)%>%
         select(ID, DAY, EVENT)%>% rename(PFS=DAY, PFS.EVENT=EVENT)


df.exp.PFStruncation <- data.frame()

for (i in 1:1000) {
  single <- Analysis.PFS$PFS[i]
  rows_for_id <- df.exp[df.exp$ID == i, ]
  rows_for_id <- rows_for_id[rows_for_id$DAY <= single, ]
  max_row <- which.max(rows_for_id$DAY)
  rows_for_id$LAST <- ifelse(1:nrow(rows_for_id) == max_row, 1, 0)
  df.exp.PFStruncation <- bind_rows(df.exp.PFStruncation, rows_for_id)
}


df.ER <- df.exp.PFStruncation %>%
        group_by(ID) %>%
  
        mutate( EVENT = if_else(Tumor < 0.7 * TumorB, 1, 0),
                LAST=0) %>%
        group_by(ID) %>%
         # Identify the first DAY where EVENT = 1 for each ID
         mutate(first_event_day = ifelse(EVENT == 1, DAY, NA_real_)) %>%
         mutate(first_event_day = min(first_event_day, na.rm = TRUE)) %>%
         # Keep all rows where EVENT = 0 or it's the first occurrence of EVENT = 1
         filter((EVENT == 0 & DAY < first_event_day) | (EVENT == 1 & DAY == first_event_day)) %>%
         mutate(last_day = max(DAY))%>%
         mutate(LAST = if_else(DAY == last_day | EVENT == 1, 1, LAST)) %>%
         ungroup()%>%
         select(-first_event_day,-last_day)

analysis.modified <- df.ER %>% filter(LAST == 1)%>%
           mutate(  DAY = case_when(
           EVENT==1 ~ DAY,
           EVENT==0 & DAY <= Onset_day ~ DAY,
           EVENT==0 & DAY > Onset_day ~ Onset_day))%>%
           select(ID, DAY,EVENT)

df.ER.modified <- left_join(analysis.modified, df.exp, by = c("ID","DAY"))
# df.exp.3 <- df.exp%>%filter(ID==3)

df.ER_correct <-  left_join(df.ER.modified, First_day_conc, by = c("ID"))

df.ER.IDQ <-df.ER_correct %>%
  rename(avgDoseTE=avgDOSE,
         CmaxOED=Cmax,
         CtroughOED=Ctrough,
         CavgOED=Cavg,
         Cavg1WOED=Cavg1W,
         Cavg2WOED=Cavg2W,
         Cavg4WOED=Cavg4W)
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/Modified_1D_include PFS truncation/True Positive ER_Modified_DH2_HL24_ID20871_ii24_60&40&20_LDR")
write.csv(df.ER.IDQ, "df_ER_IDQ_Modified.csv", row.names = FALSE)

logistic_regression_comparison <- function(df.ER.IDQ, TRUE_DH1, TRUE_DH2, x_var, y_var) {
  # Ensure x variable is numeric for log scale
 
  ggplot() +
  
     # Logistic regression line for current dataset
    geom_smooth(data = df.ER.IDQ, aes(x = .data[[x_var]], y = .data[[y_var]], color = "Logistic Regression"), 
                method = "glm", method.args = list(family = "binomial")) +
    geom_point(data = df.ER.IDQ, aes(x = .data[[x_var]], y = .data[[y_var]]), 
               shape = "|", alpha = 0.5) +
    
      # Original True ER line for DH2
    geom_line(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH2"), size = 1.5) +
    geom_point(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH2"), size = 2) +
    geom_text(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], label = DOSE, color = "True ER_DH2"), 
              vjust = 0.8, hjust = -0.4,angle = -50, size = 3.5) +
    
    # Original True ER line for DH1
    geom_line(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH1"), size = 1.5) +
    geom_point(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH1"), size = 2) +
    geom_text(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], label = DOSE), 
              vjust = 0.2, hjust = -0.4,angle = 75, size = 3.5) +
    
    custom_theme +
    theme(
      panel.background = element_rect(fill = "white", color = "black"),
      legend.background = element_rect(fill = "transparent"),
      legend.position = c(0.3, 0.8),
      legend.title = element_blank(),
      axis.text.x = element_text(size = 12, angle = 0, hjust = 1),
      axis.text.y = element_text(size = 12),
      axis.title = element_text(size = 12),
      plot.title = element_text(size = 14, hjust = 0.5),
      plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm")
        ) +
    labs(
      x = x_var,
      y = "Probability of Event",
      title = paste("Logistic Regression -", x_var),
      color = "Model"
    ) +
    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
    coord_cartesian(xlim = c(0.1, NA)) +
    scale_x_log10(labels = custom_log_labels) +
    scale_color_manual(values = c("Logistic Regression" = "black","True ER_DH2" = "blue", "True ER_DH1" = "forestgreen"))
}

## compare the true ER for DH1 and DH2
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/Modified_1D_include PFS truncation/True Positive ER_Modified_DH2_HL24_ID20871_ii24_60&40&20_LDR")

df.ER.IDQ <- read.csv("df_ER_IDQ_Modified.csv")

Logiplot1 <- logistic_regression_comparison(df.ER.IDQ, Modified_trueER_DH1, Modified_trueER_DH2, "DOSE", "EVENT")
Logiplot2 <- logistic_regression_comparison(df.ER.IDQ, Modified_trueER_DH1, Modified_trueER_DH2, "Ctrough1D", "EVENT")
Logiplot3 <- logistic_regression_comparison(df.ER.IDQ, Modified_trueER_DH1, Modified_trueER_DH2, "Cavg1D", "EVENT")
Logiplot4 <- logistic_regression_comparison(df.ER.IDQ, Modified_trueER_DH1, Modified_trueER_DH2, "CtroughOED", "EVENT")
Logiplot5 <- logistic_regression_comparison(df.ER.IDQ, Modified_trueER_DH1, Modified_trueER_DH2, "CavgOED", "EVENT")
Logiplot6 <- logistic_regression_comparison(df.ER.IDQ, Modified_trueER_DH1, Modified_trueER_DH2, "Cavg1WOED", "EVENT")
Logiplot7 <- logistic_regression_comparison(df.ER.IDQ, Modified_trueER_DH1, Modified_trueER_DH2, "Cavg2WOED", "EVENT")
Logiplot8 <- logistic_regression_comparison(df.ER.IDQ, Modified_trueER_DH1, Modified_trueER_DH2, "CavgTE", "EVENT")

Logistic_comparison <- grid.arrange(Logiplot1, Logiplot2, Logiplot3, Logiplot4,Logiplot5,Logiplot6,Logiplot7, Logiplot8,ncol = 4)

ggsave("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/Modified_1D_include PFS truncation/True Positive ER_Modified_DH2_HL24_ID20871_ii24_60&40&20_LDR/True ER comparions_DH1&2_Modified.tiff",
      plot = Logistic_comparison, 
     width = 20, height = 8, dpi = 400, units = "in")
```

##2.2 Logistic plot_did not do the log transformation
```{r}
#input the true ER relationship dataset
##input the true ER for dose DH1
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/True ER relationship/DH1")
True.ER <- read.csv("True ER_ORR.csv")
True.ER$avgDoseTE <- True.ER$DOSE

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/True ER relationship/DH2_LDR")

TrueER_DH2 <- read.csv("True ER_ORR_LDR_DH2.csv")
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/Modified_1D_include PFS truncation/True Positive ER_Modified_DH2_HL24_ID20871_ii24_60&40&20_LDR")
df.ER.IDQ <- read.csv("df_ER_IDQ_Modified.csv")

covariates <- c("Ctrough1D", "Cavg1D","CtroughOED", "CavgOED", "Cavg1WOED","CavgTE")
logistic_formulas <- sapply(covariates, function(x) as.formula(paste('EVENT ~', x)))
logistic_Results_plot <- lapply(logistic_formulas, function(formula) {
  # Fit the model
  model <- glm(formula, family = binomial(logit), data = df.ER.IDQ)
  
  # Get predicted values on the scale of log-odds (link = "logit") and convert to probabilities
  predictions <- predict(model, type = "link", se.fit = TRUE)
  
  # Confidence intervals for predictions
  lower_bound <- predictions$fit - 1.96 * predictions$se.fit
  upper_bound <- predictions$fit + 1.96 * predictions$se.fit
  
  # Convert to probability scale
  predicted_prob <- plogis(predictions$fit)
  lower_prob <- plogis(lower_bound)
  upper_prob <- plogis(upper_bound)
  
  # Return a data frame with the covariate values, predictions, and confidence intervals
  data.frame(
    Covariate = df.ER.IDQ[[all.vars(formula)[2]]],  # Extract covariate values
    Predicted_Prob = predicted_prob,
    Lower_Bound = lower_prob,
    Upper_Bound = upper_prob
  )
})

wb <- createWorkbook()
for (i in seq_along(covariates)) {
  addWorksheet(wb, covariates[i])  # Create a sheet named after the covariate
  writeData(wb, sheet = covariates[i], logistic_Results_plot [[i]])  # Write the data frame to the sheet
}

summary(logistic_Results_plot)
# Save the workbook to a file
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/Modified_1D_include PFS truncation/True Positive ER_Modified_DH2_HL24_ID20871_ii24_60&40&20_LDR")
saveWorkbook(wb, "logistic_regression_results_nolog_Modified.xlsx", overwrite = TRUE)

# logistic_regression_comparison <- function(df, TRUE_DH1, TRUE_DH2, x_var, y_var) {
#   # Ensure x variable is numeric for log scale
#  
#   ggplot() +
#   
#      # Logistic regression line for current dataset
#     geom_line(data = df, aes(x = Covariate, y = Predicted_Prob, color = "Logistic Regression"), size=1.5) +
#     geom_ribbon(data = df, aes( x = Covariate, ymin = Lower_Bound, ymax = Upper_Bound), alpha = 0.2, fill = "black") +
#     
#       # Original True ER line for DH2
#     geom_line(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH2"), size = 1.5) +
#     geom_point(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH2"), size = 2) +
#     geom_text(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], label = DOSE, color = "True ER_DH2"), 
#               vjust = 0.8, hjust = -0.4,angle = -50, size = 3.5) +
#     
#     # Original True ER line for DH1
#     geom_line(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH1"), size = 1.5) +
#     geom_point(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH1"), size = 2) +
#     geom_text(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], label = DOSE), 
#               vjust = 0.2, hjust = -0.4,angle = 75, size = 3.5) +
#     
#     custom_theme +
#     theme(
#       panel.background = element_rect(fill = "white", color = "black"),
#       legend.background = element_rect(fill = "transparent"),
#       legend.position = c(0.3, 0.8),
#       legend.title = element_blank(),
#       axis.text.x = element_text(size = 12, angle = 0, hjust = 1),
#       axis.text.y = element_text(size = 12),
#       axis.title = element_text(size = 12),
#       plot.title = element_text(size = 14, hjust = 0.5),
#       plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm")
#         ) +
#     labs(
#       x = x_var,
#       y = "Probability of ORR Event",
#       title = paste("Logistic Regression -", x_var),
#       color = "Model"
#     ) +
#    coord_cartesian(ylim = c(0, 1), xlim = c(0.1, NA))+
#     scale_y_continuous(breaks = seq(0, 1, 0.2)) +
#     scale_x_log10(labels = custom_log_labels) +
#     scale_color_manual(values = c("Logistic Regression" = "black","True ER_DH2" = "blue", "True ER_DH1" = "forestgreen"))
# }
# 
# ## compare the true ER for DH1 and DH2
# 
# 
# Logiplot1 <- logistic_regression_comparison(logistic_Results_plot$Ctrough1D, True.ER, TrueER_DH2, "Ctrough1D", "EVENT")
# Logiplot2 <- logistic_regression_comparison(logistic_Results_plot$Cavg1D, True.ER, TrueER_DH2, "Cavg1D", "EVENT")
# Logiplot3 <- logistic_regression_comparison(logistic_Results_plot$CtroughOED, True.ER, TrueER_DH2, "CtroughOED", "EVENT")
# Logiplot4 <- logistic_regression_comparison(logistic_Results_plot$CavgOED, True.ER, TrueER_DH2, "CavgOED", "EVENT")
# Logiplot5 <- logistic_regression_comparison(logistic_Results_plot$Cavg1WOED, True.ER, TrueER_DH2, "Cavg1WOED", "EVENT")
# Logiplot6 <- logistic_regression_comparison(logistic_Results_plot$CavgTE, True.ER, TrueER_DH2, "CavgTE", "EVENT")
# 
# Logistic_comparison <- grid.arrange(Logiplot1, Logiplot2, Logiplot3, Logiplot4,Logiplot5,Logiplot6,ncol = 3)
# 
# ggsave("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/Modified_1D_include PFS truncation/True Positive ER_Modified_DH2_HL24_ID20871_ii24_60&40&20_LDR/True ER comparions_DH1&2_Modified_nolog.tiff",
#       plot = Logistic_comparison, 
#      width = 15, height = 8, dpi = 400, units = "in")

```
##2.3 Logistic plot_ do the log transformation
```{r}
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/True ER relationship/DH1")
True.ER <- read.csv("True ER_ORR.csv")
True.ER$avgDoseTE <- True.ER$DOSE

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/True ER relationship/DH2_LDR")
TrueER_DH2 <- read.csv("True ER_ORR_LDR_DH2.csv")

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/Modified_1D_include PFS truncation/True Positive ER_Modified_DH2_HL24_ID20871_ii24_60&40&20_LDR")
df.ER.IDQ <- read.csv("df_ER_IDQ_Modified.csv")

covariates <- c("Ctrough1D", "Cavg1D","CtroughOED", "CavgOED", "Cavg1WOED","Cavg2WOED" , "CavgTE")
logistic_formulas <- sapply(covariates, function(x) as.formula(paste('EVENT ~ log(', x, ')')))

logistic_Results_plot <- lapply(logistic_formulas, function(formula) {
  # Fit the model
  model <- glm(formula, family = binomial(logit), data = df.ER.IDQ)
  
  # Get predicted values on the scale of log-odds (link = "logit") and convert to probabilities
  predictions <- predict(model, type = "link", se.fit = TRUE)
  
  # Confidence intervals for predictions
  lower_bound <- predictions$fit - 1.96 * predictions$se.fit
  upper_bound <- predictions$fit + 1.96 * predictions$se.fit
  
  # Convert to probability scale
  predicted_prob <- plogis(predictions$fit)
  lower_prob <- plogis(lower_bound)
  upper_prob <- plogis(upper_bound)
  
  # Return a data frame with the covariate values, predictions, and confidence intervals
  data.frame(
    Covariate = df.ER.IDQ[[all.vars(formula)[2]]],  # Extract covariate values
    Predicted_Prob = predicted_prob,
    Lower_Bound = lower_prob,
    Upper_Bound = upper_prob
  )
})

wb <- createWorkbook()
for (i in seq_along(covariates)) {
  addWorksheet(wb, covariates[i])  # Create a sheet named after the covariate
  writeData(wb, sheet = covariates[i], logistic_Results_plot [[i]])  # Write the data frame to the sheet
}

# summary(logistic_Results_plot)
# Save the workbook to a file
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/Modified_1D_include PFS truncation/True Positive ER_Modified_DH2_HL24_ID20871_ii24_60&40&20_LDR")
saveWorkbook(wb, "logistic_regression_results_log_Modified.xlsx", overwrite = TRUE)

# logistic_regression_comparison <- function(df, TRUE_DH1, TRUE_DH2, x_var, y_var) {
#   # Ensure x variable is numeric for log scale
#  
#   ggplot() +
#   
#      # Logistic regression line for current dataset
#     geom_line(data = df, aes(x = Covariate, y = Predicted_Prob, color = "Logistic Regression"), size=1.5) +
#     geom_ribbon(data = df, aes( x = Covariate, ymin = Lower_Bound, ymax = Upper_Bound), alpha = 0.2, fill = "black") +
#     
#       # Original True ER line for DH2
#     geom_line(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH2"), size = 1.5) +
#     geom_point(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH2"), size = 2) +
#     geom_text(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], label = DOSE, color = "True ER_DH2"), 
#               vjust = 0.8, hjust = -0.4,angle = -50, size = 3.5) +
#     
#     # Original True ER line for DH1
#     geom_line(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH1"), size = 1.5) +
#     geom_point(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH1"), size = 2) +
#     geom_text(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], label = DOSE), 
#               vjust = 0.2, hjust = -0.4,angle = 75, size = 3.5) +
#     
#     custom_theme +
#     theme(
#       panel.background = element_rect(fill = "white", color = "black"),
#       legend.background = element_rect(fill = "transparent"),
#       legend.position = c(0.3, 0.8),
#       legend.title = element_blank(),
#       axis.text.x = element_text(size = 12, angle = 0, hjust = 1),
#       axis.text.y = element_text(size = 12),
#       axis.title = element_text(size = 12),
#       plot.title = element_text(size = 14, hjust = 0.5),
#       plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm")
#         ) +
#     labs(
#       x = x_var,
#       y = "Probability of ORR Event",
#       title = paste("Logistic Regression -", x_var),
#       color = "Model"
#     ) +
#    coord_cartesian(ylim = c(0, 1), xlim = c(0.1, NA))+
#     scale_y_continuous(breaks = seq(0, 1, 0.2)) +
#     scale_x_log10(labels = custom_log_labels) +
#     scale_color_manual(values = c("Logistic Regression" = "black","True ER_DH2" = "blue", "True ER_DH1" = "forestgreen"))
# }
# 
# ## compare the true ER for DH1 and DH2
# 
# Logiplot1 <- logistic_regression_comparison(logistic_Results_plot$Ctrough1D, True.ER, TrueER_DH2, "Ctrough1D", "EVENT")
# Logiplot2 <- logistic_regression_comparison(logistic_Results_plot$Cavg1D, True.ER, TrueER_DH2, "Cavg1D", "EVENT")
# Logiplot3 <- logistic_regression_comparison(logistic_Results_plot$CtroughOED, True.ER, TrueER_DH2, "CtroughOED", "EVENT")
# Logiplot4 <- logistic_regression_comparison(logistic_Results_plot$CavgOED, True.ER, TrueER_DH2, "CavgOED", "EVENT")
# Logiplot5 <- logistic_regression_comparison(logistic_Results_plot$Cavg1WOED, True.ER,TrueER_DH2, "Cavg1WOED", "EVENT")
# Logiplot6 <- logistic_regression_comparison(logistic_Results_plot$CavgTE, True.ER, TrueER_DH2, "CavgTE", "EVENT")
# 
# Logistic_comparison <- grid.arrange(Logiplot1, Logiplot2, Logiplot3, Logiplot4,Logiplot5,Logiplot6,ncol = 3)
# 
# ggsave("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/Modified_1D_include PFS truncation/True Positive ER_Modified_DH2_HL24_ID20871_ii24_60&40&20_LDR/True ER comparions_DH1&2_Modified_log.tiff",
#       plot = Logistic_comparison, 
#      width = 15, height = 8, dpi = 400, units = "in")
```

#3 model comparision
```{r}
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/Modified_1D_include PFS truncation/True Positive ER_Modified_DH2_HL24_ID20871_ii24_60&40&20_LDR")
df.ER.IDQ <- read.csv( "df_ER_IDQ_Modified.csv")

covariates <- c( "Ctrough1D", "Cavg1D","CtroughOED", "CavgOED", "Cavg1WOED","CavgTE")

logistic_formulas <- sapply(covariates, function(x) as.formula(paste('EVENT ~', x)))
logistic_Results <- lapply(logistic_formulas, function(x) glm(x, family = binomial(logit), data = df.ER.IDQ))
logistic_result  <- logistic_analysis(logistic_Results,covariates)%>% 
                    rownames_to_column(var = "Variable")


logistic_formulas_log <- sapply(covariates, function(x) as.formula(paste('EVENT ~ log(', x, ')')))
logistic_Results_log <- lapply(logistic_formulas_log, function(x) glm(x, family = binomial(logit), data = df.ER.IDQ))
logistic_result_log  <- logistic_analysis(logistic_Results_log,covariates)%>% 
                    rownames_to_column(var = "Variable")

wb_model <- createWorkbook()
addWorksheet(wb_model, "log transform")
addWorksheet(wb_model, "no log transform")


writeData(wb_model, sheet = "log transform", x = logistic_result_log)
writeData(wb_model, sheet = "no log transform", x = logistic_result)

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/Modified_1D_include PFS truncation/True Positive ER_Modified_DH2_HL24_ID20871_ii24_60&40&20_LDR")
saveWorkbook(wb_model, file = "model comparison_Modified.xlsx", overwrite = TRUE)
```
#4 Incorporate the observed values to compare the model performance 
```{r}
quantiles_Five <- function(data, column_name, labels = c("1", "2", "3", "4", "5")) {
  quantiles <- quantile(data[[column_name]], probs = seq(0.2, 0.8, by = 0.2))
  categorized_column <- cut(data[[column_name]],
                            breaks = c(-Inf, quantiles, Inf),
                            labels = labels,
                            include.lowest = TRUE)
  return(categorized_column)
}

my.theme = theme_bw() +
  theme(plot.background  = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text      = element_text(size = 7),
        legend.title     = element_text(size = 7),
        axis.title       = element_text(size = 18),
        axis.text        = element_text(size = 12),
        legend.key.width = unit(.5,"cm"))

create_covariate_plot <- function(covariate_name) {
  # Read data
  setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/Modified_1D_include PFS truncation/True Positive ER_Modified_DH2_HL24_ID20871_ii24_60&40&20_LDR")
  file_path <- "logistic_regression_results_nolog_Modified.xlsx"
  Prediction <- read_excel(file_path, sheet = covariate_name)
  
   setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/Modified_1D_include PFS truncation/True Positive ER_Modified_DH2_HL24_ID20871_ii24_60&40&20_LDR")
  file_path <- "logistic_regression_results_log_Modified.xlsx"
  Prediction_log <- read_excel(file_path, sheet = covariate_name)
  
  # Calculate statistics
  covariate_stats <- quantile(df.ER.IDQ[[covariate_name]], probs = c(0.05, 0.5, 0.95), na.rm = TRUE)
  names(covariate_stats) <- c("p05", "med", "p95")
  
  # Prepare plot data
  eff.stats <- df.ER.IDQ %>%
    group_by(!!sym(paste0(covariate_name, "_IDQ"))) %>%
    summarise(N = n(),
              NResp = sum(EVENT == 1),
              Minimum = min(!!sym(covariate_name)),
              Median = median(!!sym(covariate_name)),
              Maximum = max(!!sym(covariate_name)),
              ObsProb = round(NResp / N, 4)) %>%
    mutate(bins = paste0(row_number(), "^", c("st", "nd", "rd", rep("th", n() - 3)), "^ quartile")) %>%
    select(bins, N, Minimum, Median, Maximum, NResp, ObsProb) %>%
    group_by(bins) %>%
    mutate(exact.lower = binom.test(NResp, N)$conf.int[1],
           exact.upper = binom.test(NResp, N)$conf.int[2]) %>%
    as.data.frame()
  
  # Create plot
  p <- ggplot() +
    geom_jitter(data = df.ER.IDQ, aes(x = !!sym(covariate_name), y = EVENT, color = "Observation"), alpha = 0.2, size = 1, height = 0.03) +
    
       # Original True ER line for DH2
    geom_line(data = TRUE_DH2, aes(x = !!sym(covariate_name), y =  EVENT, color = "True ER_DH2"), size = 1.5) +
    geom_point(data = TRUE_DH2, aes(x = !!sym(covariate_name), y =  EVENT, color = "True ER_DH2"), size = 2) +
    geom_text(data = TRUE_DH2, aes(x = !!sym(covariate_name), y =  EVENT, label = DOSE, color = "True ER_DH2"), 
              vjust = 0.8, hjust = -0.4,angle = -50, size = 3.5) +
    
    # Original True ER line for DH1
    geom_line(data = TRUE_DH1, aes(x = !!sym(covariate_name), y =  EVENT, color = "True ER_DH1"), size = 1.5) +
    geom_point(data = TRUE_DH1, aes(x = !!sym(covariate_name), y =  EVENT, color = "True ER_DH1"), size = 2) +
    geom_text(data = TRUE_DH1, aes(x = !!sym(covariate_name), y =  EVENT, label = DOSE), 
              vjust = 0.2, hjust = -0.4,angle = 75, size = 3.5) +
    
    
    geom_line(data = Prediction, aes(x = Covariate, y = Predicted_Prob, color = "No log transformation"), size = 1.5) +
    geom_ribbon(data = Prediction, aes(x = Covariate, ymin = Lower_Bound, ymax = Upper_Bound), alpha = 0.2, fill = "#00BFC4") +
    
    
    geom_line(data = Prediction_log, aes(x = Covariate, y = Predicted_Prob, color = "Log transformation"), size = 1.5) +
    geom_ribbon(data = Prediction_log, aes(x = Covariate, ymin = Lower_Bound, ymax = Upper_Bound), alpha = 0.2, fill = "#F8766D") +
    
    geom_errorbar(data = eff.stats, aes(x = Median, ymin = exact.lower, ymax = exact.upper), size = 1.1, width = 0.1) +
    geom_point(data = eff.stats, aes(x = Median, y = ObsProb), size = 2) +
    geom_segment(aes(x = min(eff.stats$Minimum), xend = max(eff.stats$Maximum), y = -0.05, yend = -0.05), size = 1.1) +
    geom_segment(data = eff.stats, aes(x = Minimum, xend = Minimum, y = -0.07, yend = -0.03), size = 1.1) +
    geom_segment(data = eff.stats[nrow(eff.stats), ], aes(x = Maximum, xend = Maximum, y = -0.07, yend = -0.03), size = 1.1) +
    geom_vline(xintercept = covariate_stats["med"], linetype = 'solid') +
    geom_vline(xintercept = covariate_stats["p05"], linetype = 'dashed') +
    geom_vline(xintercept = covariate_stats["p95"], linetype = 'dashed') +
    scale_color_manual(values = c("Observation" = "black", "No log transformation" = "#00BFC4", "Log transformation" = "#F8766D","True ER_DH2" = "blue", "True ER_DH1" = "forestgreen")) +
    my.theme +
    xlab(covariate_name) + 
    ylab("Probability of Responder") +
    ggtitle(paste("Model comparison: log vs no log -", covariate_name)) +
    theme(
      legend.position = c(0.7, 0.3),
      legend.background = element_rect(fill = "transparent"),
      legend.title = element_blank(),
      legend.text = element_text(size = 9),
      legend.key.size = unit(0.5, "cm"),
      axis.text.x = element_text(size = 12, angle = 0, hjust = 1),
      axis.text.y = element_text(size = 12),
      axis.title = element_text(size = 12),
      plot.title = element_text(size = 14, hjust = 0.5),
      plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm")
    )
  
  return(p)
}

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/True ER relationship/DH1")
TRUE_DH1 <- read.csv("True ER_ORR.csv")
TRUE_DH1$avgDoseTE <- TRUE_DH1$DOSE

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/True ER relationship/DH2_LDR")
TRUE_DH2 <- read.csv("True ER_ORR_LDR_DH2.csv")

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/Modified_1D_include PFS truncation/True Positive ER_Modified_DH2_HL24_ID20871_ii24_60&40&20_LDR")
df.ER.IDQ <- read.csv("df_ER_IDQ_Modified.csv")

df.ER.IDQ$Ctrough1D_IDQ  <- quantiles_Five(df.ER.IDQ, "Ctrough1D")
df.ER.IDQ$CtroughOED_IDQ  <- quantiles_Five(df.ER.IDQ, "CtroughOED")
df.ER.IDQ$Cavg1D_IDQ  <- quantiles_Five(df.ER.IDQ, "Cavg1D")
df.ER.IDQ$CavgOED_IDQ  <- quantiles_Five(df.ER.IDQ, "CavgOED")
df.ER.IDQ$Cavg1WOED_IDQ  <- quantiles_Five(df.ER.IDQ, "Cavg1WOED")
df.ER.IDQ$Cavg2WOED_IDQ  <- quantiles_Five(df.ER.IDQ, "Cavg2WOED")
df.ER.IDQ$CavgTE_IDQ  <- quantiles_Five(df.ER.IDQ, "CavgTE")

plot_Ctrough1D <- create_covariate_plot("Ctrough1D")
plot_Cavg1D <- create_covariate_plot("Cavg1D")
plot_Cavg1WOED <- create_covariate_plot("Cavg1WOED")
plot_CtroughOED <- create_covariate_plot("CtroughOED")
plot_CavgOED <- create_covariate_plot("CavgOED")
plot_CavgTE <- create_covariate_plot("CavgTE")

plot_Ctrough1D_L <- create_covariate_plot("Ctrough1D")+ scale_x_log10(labels = custom_log_labels) + coord_cartesian(ylim = c(0, 1), xlim = c(0.1, NA))+ theme(legend.position = c(0.3, 0.7))
plot_Cavg1D_L <- create_covariate_plot("Cavg1D")+ scale_x_log10(labels = custom_log_labels) + coord_cartesian(ylim = c(0, 1), xlim = c(0.1, NA))+ theme(legend.position = c(0.3, 0.7))
plot_Cavg1WOED_L <- create_covariate_plot("Cavg1WOED")+ scale_x_log10(labels = custom_log_labels) + coord_cartesian(ylim = c(0, 1), xlim = c(0.1, NA))+ theme(legend.position = c(0.3, 0.7))
plot_CtroughOED_L <- create_covariate_plot("CtroughOED")+ scale_x_log10(labels = custom_log_labels) + coord_cartesian(ylim = c(0, 1), xlim = c(0.1, NA))+ theme(legend.position = c(0.3, 0.7))
plot_CavgOED_L <- create_covariate_plot("CavgOED")+ scale_x_log10(labels = custom_log_labels) + coord_cartesian(ylim = c(0, 1), xlim = c(0.1, NA))+ theme(legend.position = c(0.3, 0.7))
plot_CavgTE_L <- create_covariate_plot("CavgTE")+ scale_x_log10(labels = custom_log_labels) + coord_cartesian(ylim = c(0, 1), xlim = c(0.1, NA))+ theme(legend.position = c(0.3, 0.7))

model_comparison <- grid.arrange(plot_Ctrough1D, plot_Cavg1D, plot_Cavg1WOED, plot_CtroughOED,plot_CavgOED,plot_CavgTE,ncol = 3)
ggsave("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/Modified_1D_include PFS truncation/True Positive ER_Modified_DH2_HL24_ID20871_ii24_60&40&20_LDR/model comparision results_linear_5.tiff",
      plot = model_comparison, 
     width = 15, height = 8, dpi = 400, units = "in")

model_comparison_L <- grid.arrange(plot_Ctrough1D_L, plot_Cavg1D_L, plot_Cavg1WOED_L, plot_CtroughOED_L,plot_CavgOED_L,plot_CavgTE_L,ncol = 3)
ggsave("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis_manuscript1/Modified_1D_include PFS truncation/True Positive ER_Modified_DH2_HL24_ID20871_ii24_60&40&20_LDR/model comparision results_log_5.tiff",
      plot = model_comparison_L, 
     width = 15, height = 8, dpi = 400, units = "in")

```
