---
title: "True Positive ORR_with dynamic dose modification"
author: "Xuefen Yin"
date: "2024-8-8"
output: pdf_document
---

# R setup
```{r setup, echo = F}

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

rm(list=ls(all=TRUE))

library(tidyverse)
library(mrgsolve)
library(ggplot2)
library(survival)
library(survminer)
library(gridExtra)
library(muhaz)
library(zoo)
library(ggExtra)
library(patchwork)
library(ggridges)
library(purrr)
library(grid)
library(cowplot)
library(openxlsx)
library(brms) ## Emax
library(broom)
library(readxl)
new_path <- paste("C:/rtools40/usr/bin", "C:/rtools40/mingw64/bin", Sys.getenv("PATH"), sep=";")
Sys.setenv(PATH = new_path)

theme_set(theme_bw())
```
#1 Common functions(run one time)

Note: Need to combine the plotting functions when all details are settle down

##1.1 common function for data visualization 

```{r}
custom_log_labels <- function(x) {
  ifelse(x < 10, 
         sprintf("%.1f", x),  # One decimal place for numbers < 10
         sprintf("%.0f", x))  # No decimal places for numbers >= 10
}

custom_theme <- theme_classic() +
  theme(
    panel.grid.major = element_line(color = "gray70", linewidth = 0.5),  # Major grid lines
    panel.grid.minor = element_line(color = "gray90", linewidth = 0.25)  # Minor grid lines
  )

# General KM plot function
KM_plot_G <- function(km_object, data, title_prefix, group_labels, colors, plot_x_scale = 600, save_path) {

    if (length(group_labels) != length(colors)) {
    stop("The length of group_labels and colors must be the same")
  }
  
  plot <- ggsurvplot(
    km_object,
    data = data,
    surv.median.line = "hv",
    conf.int = TRUE,
    #pval = TRUE,
    #pval.method = TRUE,
    risk.table = TRUE,
    risk.table.y.text = FALSE,
    tables.theme = theme_cleantable(),
    tables.height = 0.25,
    palette = colors,
    legend.labs = group_labels,
    xlim = c(0, plot_x_scale),
    legend.title = element_blank() 
  ) + labs(
    y = "Probability of No Event",
    x = "Days",
    title = paste("True ER relationship -", title_prefix)
  )

  plot$plot <- plot$plot +
    theme(plot.subtitle = element_text(size = 10)) +
    scale_x_continuous(breaks = seq(0, plot_x_scale, by = 50))
  
  
  if (identical(data, analysis)) {
    ggsave(filename = save_path, plot = plot$plot, width = 7, height = 5, dpi = 400, units = "in")
  }
    
  return(plot)
}


# KM plot function containing saving function
KM_plot_Q <- function(km_object, data, title_prefix,group_labels, colors,plot_x_scale = 600, save_path) {
  plot <- ggsurvplot(
    km_object,
    data = data,
    surv.median.line = "hv",
    conf.int = TRUE,
    #pval = TRUE,
   # pval.method = TRUE,
    risk.table = TRUE,
    risk.table.y.text = FALSE,
    tables.theme = theme_cleantable(),
    tables.height = 0.25,
    palette = colors,
    legend.labs = group_labels,
    xlim = c(0, plot_x_scale),
    legend.title = element_blank() 
  )+ labs( y = "Probability of No Event",
           x = "Days",
          title = paste("True ER relationship -",title_prefix)) 

   plot$plot <- plot$plot +
   theme(plot.subtitle = element_text(size = 10))+
   scale_x_continuous(breaks = seq(0, plot_x_scale, by = 50))
   
  # # Save the plot
   ggsave(filename = save_path, plot = plot$plot, width = 7, height = 5, dpi = 400, units = "in")
  
  return(plot)
}

###KM plot with no strata

KM_plot <- function(km_object, data, title_prefix,plot_x_scale = 600, save_path) {
    plot <- ggsurvplot(
    km_object,
    data = data,
    surv.median.line = "hv",
    color = "black",
    conf.int.fill = "grey45",
    conf.int = TRUE,
    title = paste("True ER -",title_prefix),
    xlab = "Days",
    ylab = "Probability of no event",
    xlim = c(0, plot_x_scale),
    risk.table = "abs_pct",
    risk.table.y.text = FALSE,
    cumcensor = TRUE,
    tables.theme = theme_cleantable(),
    tables.height = 0.15,
    legend = "none"
  )
  
  plot$plot <- plot$plot +
    theme(
      plot.title = element_text(size = 14),
      plot.subtitle = element_text(size = 12),
      axis.title = element_text(size = 14),
      axis.text = element_text(size = 12)
    ) +
    scale_x_continuous(breaks = seq(0, plot_x_scale, by = 50)) +
    theme(
      plot.title = element_text(hjust = 0.5),
     # axis.text.x = element_text(angle = 60)
    )
  
  # # Save the plot
   ggsave(filename = save_path, plot = plot$plot, width = 5, height = 4, dpi = 400, units = "in")
   
  return(plot)
}


# comparing tumor size change with the dose change
Tumor_Dose_plot <- function(id, data, response_duration, pfs_linear) {
  data <- data %>%
    filter(ID == id) 
  first_day <- response_duration$First_Response_Day[response_duration$ID == id]
  last_day <- response_duration$Last_Response_Day[response_duration$ID == id]
  pfs_day <- pfs_linear$DAY[pfs_linear$ID == id]
  
  max_tumor <- max(data$Tumor, na.rm = TRUE)
  max_dose <- max(data$DOSE, na.rm = TRUE)
  
  p <- ggplot(data, aes(x = DAY)) +
    geom_point(aes(y = DOSE / max_dose * max_tumor), color = "springgreen4", size = 1) +
    geom_line(aes(y = Tumor), size = 1.5, color = "black") +
    geom_line(aes(y = TumorB * 1.2), linetype = "dashed", color = "red", size = 0.5) +
    geom_line(aes(y = TumorB * 0.7), linetype = "dashed", color = "navyblue", size = 0.5) +
    theme_classic() +
    geom_vline(xintercept = first_day, color = "navyblue") +
    annotate("text", x = first_day, y = max_tumor * 0.75, label = as.character(first_day), vjust = 1.2, hjust = 0, size = 3, angle = 0, color = "navyblue", fontface = "bold") +
    geom_vline(xintercept = last_day, color = "navyblue") +
    annotate("text", x = last_day, y = max_tumor, label = as.character(last_day), vjust = 1.2, hjust = 0, size = 3, angle = 0, color = "navyblue", fontface = "bold") +
    geom_vline(xintercept = pfs_day, color = "red") +
    annotate("text", x = pfs_day, y = max_tumor * 0.75, label = as.character(pfs_day), vjust = 1.2, hjust = 0, size = 3, angle = 0, color = "red", fontface = "bold") +
    labs(
      x = "Time (Days)",
      y = "Tumor size (mm)",
      title = paste("ID-", id)
    ) +
    scale_y_continuous(
      name = "Tumor size (mm)",
      sec.axis = sec_axis(~ . * max_dose  / max_tumor, name = "Dose (mg)", 
                          breaks = seq(0, max_dose , by = 20)),
      limits = c(0, NA)
    ) +
    theme(
      panel.background = element_rect(fill = "white", color = "black"),
      panel.grid.major.y = element_line(color = "grey"),
      panel.grid.minor.x = element_line(color = "grey", linetype = 2),
      panel.grid.major.x = element_line(color = "grey"),
      legend.background = element_rect(fill = "transparent"),
      axis.text.x = element_text(size = 8, angle = 0),
      axis.text.y = element_text(size = 8),
      plot.title = element_text(hjust = 0.5)
    )
  
  return(p)
}

# comparing tumor size change with the exposure metrics change
PKPD_profile_plot <- function(id, data, response_duration, pfs_linear) {
  data <- data %>% filter(ID == id) 
  first_day <- response_duration$First_Response_Day[response_duration$ID == id]
  last_day <- response_duration$Last_Response_Day[response_duration$ID == id]
  pfs_day <- pfs_linear$DAY[pfs_linear$ID == id]
  
  max_tumor <- max(data$Tumor, na.rm = TRUE)
  max_CP <- max(data$CP, na.rm = TRUE)
  min_CP <- min(data$CP[data$CP > 0], na.rm = TRUE)  # Minimum non-zero CP value
  
  p <- ggplot(data, aes(x = DAY)) +
    geom_point(aes(y = scales::rescale(log10(CP), to = c(0, max_tumor))), color = "springgreen4", size = 1) +
    geom_line(aes(y = Tumor), size = 1.5, color = "black") +
    geom_line(aes(y = TumorB * 1.2), linetype = "dashed", color = "red", size = 0.5) +
    geom_line(aes(y = TumorB * 0.7), linetype = "dashed", color = "navyblue", size = 0.5) +
    theme_classic() +
    geom_vline(xintercept = first_day, color = "navyblue") +
    annotate("text", x = first_day, y = max_tumor * 0.75, label = as.character(first_day), vjust = 1.2, hjust = 0, size = 3, angle = 0, color = "navyblue", fontface = "bold") +
    geom_vline(xintercept = last_day, color = "navyblue") +
    annotate("text", x = last_day, y = max_tumor, label = as.character(last_day), vjust = 1.2, hjust = 0, size = 3, angle = 0, color = "navyblue", fontface = "bold") +
    geom_vline(xintercept = pfs_day, color = "red") +
    annotate("text", x = pfs_day, y = max_tumor * 0.75, label = as.character(pfs_day), vjust = 1.2, hjust = 0, size = 3, angle = 0, color = "red", fontface = "bold") +
    labs(
      x = "Time (Days)",
      y = "Tumor size (mm)",
      title = paste("ID-", id)
    ) +
    scale_y_continuous(
      name = "Tumor size (mm)",
      sec.axis = sec_axis(
        ~ 10^(. * (log10(max_CP) - log10(min_CP)) / max_tumor + log10(min_CP)),
        name = "Plasma concentration (ng/ml)",
        breaks = scales::trans_breaks("log10", function(x) 10^x),
        labels = scales::trans_format("log10", scales::math_format(10^.x))
      ),
      limits = c(0, NA)
    ) +
    theme(
      panel.background = element_rect(fill = "white", color = "black"),
      panel.grid.major.y = element_line(color = "grey"),
      panel.grid.minor.x = element_line(color = "grey", linetype = 2),
      panel.grid.major.x = element_line(color = "grey"),
      legend.background = element_rect(fill = "transparent"),
      axis.text.x = element_text(size = 8, angle = 0),
      axis.text.y = element_text(size = 8),
      plot.title = element_text(hjust = 0.5)
    )
  
  return(p)
}

# plot time-exposure metrics profile
Typical_plot_DH2 <- function(data, y_var, title) {
  ggplot(data, aes(x = DAY, y = !!sym(y_var), color = as.factor(ID))) +
    geom_point() +
    geom_line() +
    theme_classic() +
    theme(
      panel.background = element_rect(fill = "white"),
      panel.grid.major.y = element_line(color = "grey"),
      panel.grid.minor.x = element_line(color = "grey", linetype = 2),
      panel.grid.major.x = element_line(color = "grey"),
      legend.background = element_rect(fill = "transparent"),
      plot.title = element_text(hjust = 0.5),
      legend.key.size = unit(0.5, "lines"), # Reduce the legend key size
      legend.text = element_text(size = 6) # Reduce the legend text size
    ) +
    scale_color_brewer(palette = "Paired") +
    labs(x = "Time (days)",
         y = y_var,
         title = title,
         color = "ID")
}



# genetate plot of PK using ID having the median Ctrough at the end of first doing interval
CP_plot <- function(data, title) {
  ggplot(data, aes(x = time, y = CP, color = as.factor(ID))) +
    geom_point() +
    geom_line() +
    scale_y_log10() +
    theme_classic() +
    theme(
      panel.background = element_rect(fill = "white"),
      panel.grid.major.y = element_line(color = "grey"),
      panel.grid.minor.x = element_line(color = "grey", linetype = 2),
      panel.grid.major.x = element_line(color = "grey"),
      legend.background = element_rect(fill = "transparent"),
      plot.title = element_text(hjust = 0.5)
    ) +
    scale_color_brewer(palette = "Paired") +
    labs(x = "Time (hours)", y = "Concentration", title = title, color = "ID")
}


logistic_regression_PK <- function(summary_data, combined_data, df.ER.IDQ, x_var, y_var) {
  # Ensure x variable is numeric for log scale
  combined_data[[x_var]] <- as.numeric(combined_data[[x_var]])
  
  ggplot() +
  
       # True ER Logistic regression line
    geom_smooth(data = combined_data, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER Logistic Regression"), 
                method = "glm", method.args = list(family = "binomial")) +
    geom_point(data = combined_data, aes(x = .data[[x_var]], y = .data[[y_var]]), 
               shape = "|", alpha = 0.5) +
   
     # Logistic regression line for current dataset
    geom_smooth(data = df.ER.IDQ, aes(x = .data[[x_var]], y = .data[[y_var]], color = "Logistic Regression"), 
                method = "glm", method.args = list(family = "binomial")) +
    geom_point(data = df.ER.IDQ, aes(x = .data[[x_var]], y = .data[[y_var]]), 
               shape = "|", alpha = 0.5) +
    
    # Original True ER line
    geom_line(data = summary_data, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER"), size = 1.5) +
    geom_point(data = summary_data, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER"), size = 2) +
    geom_text(data = summary_data, aes(x = .data[[x_var]], y = .data[[y_var]], label = DOSE), 
              vjust = 0.2, hjust = -0.4,angle = 75, size = 3.5) +
    
    custom_theme +
    theme(
      panel.background = element_rect(fill = "white", color = "black"),
      legend.background = element_rect(fill = "transparent"),
      legend.position = c(0.3, 0.8),
      legend.title = element_blank(),
      axis.text.x = element_text(size = 12, angle = 0, hjust = 1),
      axis.text.y = element_text(size = 12),
      axis.title = element_text(size = 12),
      plot.title = element_text(size = 14, hjust = 0.5),
      plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm")
        ) +
    labs(
      x = x_var,
      y = "Probability of ORR Event",
      title = paste("Logistic Regression -", x_var),
      color = "Model"
    ) +
    coord_cartesian(ylim = c(0, 1), xlim = c(0.1, NA))+
    scale_y_continuous(breaks = seq(0, 1, 0.2)) +
    scale_x_log10(labels = custom_log_labels) +
    scale_color_manual(values = c("True ER Logistic Regression" = "blue", "Logistic Regression" = "black", "True ER" = "forestgreen"))
}

logistic_regression_PD <- function(data, predictor, response) {
  # Ensure predictor is numeric for log scale
  data[[predictor]] <- as.numeric(data[[predictor]])

  plot <- data %>%
    ggplot(aes_string(x = predictor, y = response)) +
    geom_point(shape = "|") +
    geom_smooth(method = "glm", method.args = list(family = "binomial")) +
    scale_x_log10() +
    labs(x = predictor,
         y = "Probability of Event",
         title = paste("Logistic Regression -", predictor))

  return(plot)
}

```

##1.2 common function to handle the dataset
```{r}
## split the dataset into 4 groups
quantiles <- function(data, column_name, labels = c("1", "2", "3", "4")) {
  quantiles <- quantile(data[[column_name]], probs = c(0.25, 0.5, 0.75))
  categorized_column <- cut(data[[column_name]],
                            breaks = c(-Inf, quantiles, Inf),
                            labels = labels,
                            include.lowest = TRUE)
  return(categorized_column)

}

## split the dataset into 3 groups
tertile <- function(data, column_name, labels = c("1", "2", "3")) {
  # Calculate the tertiles
  tertiles <- quantile(data[[column_name]], probs = c(1/3, 2/3))
  
  # Categorize the column based on the tertiles
  categorized_column <- cut(data[[column_name]], 
                            breaks = c(-Inf, tertiles, Inf), 
                            labels = labels, 
                            include.lowest = TRUE)
  return(categorized_column)
}

### perfrom the Mann-Whitney U-Test and save the result

wilcox <- function(df_group1, df_group2, variables) {
  # Initialize an empty data frame to store results
  results_df <- data.frame(p_value = numeric(), stringsAsFactors = FALSE)
  
  for (var in variables) {
    # Run the Wilcoxon test for the current variable
    test_result <- wilcox.test(df_group1[[var]], df_group2[[var]], paired = FALSE, alternative = "two.sided",
                               conf.int = TRUE, conf.level=0.95) # Note: corrected "confi.level" to "conf.level"
    
    # Append the variable name and p-value to the results dataframe
     temp_result <- data.frame(P.Value = test_result$p.value, stringsAsFactors = FALSE)
     rownames(temp_result) <- var
     
     results_df <- rbind(results_df, temp_result)
  }
  return(results_df)
}

### extract results from univariate Cox PH models_continuous

univ_con <- function(univ_models) {
    univ_results <- lapply(univ_models, function(x) {
    x <- summary(x)  # Summarize the model
    # Extract and format the results
    P.value <- signif(x$wald["pvalue"], digits=3)
    wald.test <- signif(x$wald["test"], digits=3)
    beta <- signif(x$coef[1], digits=3)  # Coefficient beta
    HR <- signif(exp(x$coef[1]), digits=3)  # Hazard Ratio (HR)
    HR.confint.lower <- signif(x$conf.int[,"lower .95"], 3)
    HR.confint.upper <- signif(x$conf.int[,"upper .95"], 3)
    HR <- paste0(HR, " (",
                 HR.confint.lower, "-", HR.confint.upper, ")")
    res <- c(beta, HR, wald.test, P.value)
    names(res) <- c("beta", "HR (95% CI for HR)", "wald.test", "P.Value")
    return(res)
  })
  # Convert the list of results to a dataframe
  result_df <- t(as.data.frame(univ_results))
  return(result_df)
}

### extract results from univariate Cox PH models_categorical_4 GROUP
univ_cat <- function(univ_models_G) {
  
          univ_results_G <- lapply(univ_models_G, function(x) { 
          x <- summary(x)

          # Extract Wald test p-value and statistic
          P.value<-signif(x$wald["pvalue"], digits=2)
          wald.test<-signif(x$wald["test"], digits=2)
          beta <- numeric(length = 3)
          HR <- numeric(length = 3)
          HR.confint.lower <- numeric(length = 3)
          HR.confint.upper <- numeric(length = 3)
          HRs <- character(length = 3)
  
          for (i in 1:3) {
            beta[i] <- signif(x$coef[i], digits = 3)
            HR[i] <- signif(exp(x$coef[i]), digits = 3) # HR
            HR.confint.lower[i] <- signif(x$conf.int[i,3],3)
            HR.confint.upper[i] <- signif(x$conf.int[i,4],3)
            HRs[i] <- paste0(HR[i], " (", HR.confint.lower[i], "-", HR.confint.upper[i], ")")
            }
           res <- c(beta, HRs, wald.test, P.value )
           names(res) <- c(paste0("Beta", 1:3), paste0("HR (95% CI) ", 1:3), "Wald.Test", "P.Value")
   
           return(res)

          })
          # Convert the list of results to a dataframe
          result_df <- t(as.data.frame(univ_results_G))
          return(result_df)
}  

## extract results from univariate Cox PH models_categorical_3 GROUP

univ_cat_T <- function(univ_models_G) {
  
          univ_results_G <- lapply(univ_models_G, function(x) { 
          x <- summary(x)

          # Extract Wald test p-value and statistic
          P.value<-signif(x$wald["pvalue"], digits=2)
          wald.test<-signif(x$wald["test"], digits=2)
          beta <- numeric(length = 2)
          HR <- numeric(length = 2)
          HR.confint.lower <- numeric(length = 2)
          HR.confint.upper <- numeric(length = 2)
          HRs <- character(length = 2)
  
          for (i in 1:2) {
            beta[i] <- signif(x$coef[i], digits = 3)
            HR[i] <- signif(exp(x$coef[i]), digits = 3) # HR
            HR.confint.lower[i] <- signif(x$conf.int[i,3],3)
            HR.confint.upper[i] <- signif(x$conf.int[i,4],3)
            HRs[i] <- paste0(HR[i], " (", HR.confint.lower[i], "-", HR.confint.upper[i], ")")
            }
           res <- c(beta, HRs, wald.test, P.value )
           names(res) <- c(paste0("Beta", 1:2), paste0("HR (95% CI) ", 1:2), "Wald.Test", "P.Value")
   
           return(res)

          })
          # Convert the list of results to a dataframe
          result_df <- t(as.data.frame(univ_results_G))
          return(result_df)
}  

# uni <- coxph(Surv(DAY, EVENT) ~ CtroughQ, data = df.ER)
# summary<- summary(uni)
# summary$conf.int

# extract results from univariate Cox PH models_continuous
logistic_analysis <- function(logistic_Results, covariates) {
  logistic_summaries <- lapply(logistic_Results, summary)
  
  logistic.results <- lapply(seq_along(logistic_summaries), function(i) {
    x <- logistic_summaries[[i]]
    P.value <- signif(x$coefficients[2, 4], digits=3)
    Slope <- signif(x$coefficients[2, 1], digits=3)
    AIC <- round(AIC(logistic_Results[[i]]), 1)   # Use the actual model object, not the summary
    res <- c(Slope, AIC, P.value)
    names(res) <- c("Slope","AIC", "P.Value")
    return(res)
  })
  
  # Convert the list of results to a dataframe
  result_df <- as.data.frame(do.call(rbind, logistic.results))
  row.names(result_df) <- covariates  # Add row names
  
  return(result_df)
}

Calculate_EC50_linear <- function(predictor, data) {
  
  # Initialize an empty list to store results
  EC50_results <- list()
  
  # Loop through each predictor in the predictor vector
  for (pred in predictor) {
    
    # Fit the logistic regression model
    formula <- as.formula(paste("EVENT ~", pred))
    model <- glm(formula, family="binomial", data=data)
    
    # Extract coefficients
    b0 <- coef(model)[1]
    b1 <- coef(model)[2]
    
    # Calculate EC50 and its standard error
    EC50 <- -b0 / b1
    dEC50_b0 <- -1 / b1
    dEC50_b1 <- b0 / b1^2
    dEC50_b <- matrix(c(dEC50_b0, dEC50_b1), ncol=1)
    V_EC50 <- t(dEC50_b) %*% vcov(model) %*% dEC50_b
    Std_Err <- sqrt(V_EC50)
    
    # Calculate confidence intervals
    LB <- EC50 - 1.96 * Std_Err
    UB <- EC50 + 1.96 * Std_Err
    
    # Store the results in the list
    EC50_results[[pred]] <- c(b0, b1, EC50, Std_Err, LB, UB)
  }
  
  # Convert the list to a matrix and set row and column names
  EC50_out <- do.call(rbind, EC50_results)
  colnames(EC50_out) <- c("b0", "b1", "EC50", "Std Err", "LB", "UB")
  rownames(EC50_out) <- predictor
  
  # Return the rounded results
  return(round(EC50_out, 4))
}
```

#2 Tumor growth profiles with treatment effect

Here, we directly use the df.exp dataset generated for PFS events to keep the same dosing history. The reason is that we will get the different dose modification parttern via that bionormial distribution though we use the same PKPDAE parameters 

NOTE: 
Cavg: daily average concentration
Cavg1WC1: the average concentration in the first doing cycle(1w) equals to conc at the end of the first dosing cycle.
CavgTE2WC1:similar to the Cavg1WC1, the dosing cycle is 2W.
```{r}
df.exp <- readRDS("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/PFS_2D_500ID for each arm/True inverse ER_PFS_DH2_HL24_ID20871_ii24_200&100_LDR/df_exp.rds")


DI = 1 # dose interval: DAY
Case.fix <- 2  

# HDOSE <- 500
# MDOSE <- 200
# LDOSE <- 100
# 
# # Generate dose_label
# dose_label <- c("0mg", paste0(c(LDOSE, MDOSE, HDOSE), "mg"))

# # Generate legend.labels_dose
# legend.labels_dose <- paste0("Q", 1:4, ": ", dose_label)

ids <- c(1:1000)
random_seed <- 112
set.seed(random_seed)
selected_ids <- sample(ids, 12) %>% sort()

# draw the typical tumor growth profiles
ORR_duration <- df.exp %>%
                mutate( ORR = if_else(Tumor < 0.7 * TumorB, 1, 0))%>%
                filter(ORR==1)%>%
                group_by(ID) %>%
                summarize(
                         First_Response_Day = min(DAY),
                         Last_Response_Day = max(DAY)
                         ) %>%
                filter(!is.infinite(First_Response_Day))%>%
                mutate(duration=Last_Response_Day-First_Response_Day)

PFS.time <- df.exp %>%
             mutate( PFS = if_else(Tumor < 1.2 * TumorB, 0, 1))%>%
             filter(PFS==1)%>%
             group_by(ID) %>%
             slice_min(order_by = DAY, n = 1) %>%
             ungroup()%>%
             select(ID,DAY)

ORR_duration_T <- ORR_duration%>% filter(ID %in% selected_ids)
PFS.time_T <- PFS.time%>% filter(ID %in% selected_ids)
# draw the typical tumor growth profiles

#Tumor dose plot
TG_Tumor_dose_plots <- lapply(selected_ids, Tumor_Dose_plot, data = df.exp, response_duration = ORR_duration_T, pfs_linear = PFS.time_T)
combined_Tumor_dose_plot <- wrap_plots(TG_Tumor_dose_plots, ncol = 3)

ggsave("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/Typical Tumor dose plot.tiff",
        plot = combined_Tumor_dose_plot ,
        width = 12, height = 10, dpi = 400, units = "in")

## set CP=0 if cp<0.1

 df.exp.clear <- df.exp %>% mutate(CP = if_else(CP < 0.1, 0, CP))

TG_PKPD_profile_plots <- lapply(selected_ids, PKPD_profile_plot, data = df.exp.clear, response_duration = ORR_duration_T, pfs_linear = PFS.time_T)
combined_PKPD_profile_plot <- wrap_plots(TG_PKPD_profile_plots, ncol = 3)

ggsave("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/Typical PKPD profile plot.tiff",
        plot = combined_PKPD_profile_plot,
        width = 12, height = 10, dpi = 400, units = "in")


# draw the 12IDs' exposure metric profiles
   exp.12ID <- df.exp %>%  filter(ID %in% selected_ids)

    CP.plot <- Typical_plot_DH2(exp.12ID, "CP", "Typical CP Profiles")
    Cavg.plot <- Typical_plot_DH2(exp.12ID, "Cavg", "Typical Cavg Profiles")
    Cavg1W.plot <- Typical_plot_DH2(exp.12ID, "Cavg1W", "Typical Cavg1W Profiles")
    Cavg2W.plot <- Typical_plot_DH2(exp.12ID, "Cavg2W", "Typical Cavg2W Profiles")
    Cavg4W.plot <- Typical_plot_DH2(exp.12ID, "Cavg4W", "Typical Cavg4W Profiles")
    CavgTE.plot <- Typical_plot_DH2(exp.12ID, "CavgTE", "Typical CavgTE Profiles")

    COMBINE_TP <- grid.arrange(CP.plot, Cavg.plot, Cavg1W.plot,  Cavg2W.plot, Cavg4W.plot, CavgTE.plot, ncol = 3)

    ggsave("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/Typical plots for exposure matrix.tiff",
        plot = COMBINE_TP, 
        width = 16, height = 6, dpi = 400, units = "in")

```


#3 Generate the exposure event dataset

##3.1 Based on Percentage Decrease in Tumor Size Relative to Baseline
- Have an Event if Tumor size Decrease > 30% (ORR)
- otherwise, sensored the data
```{r}
df.exp <- readRDS("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/PFS_2D_500ID for each arm/True inverse ER_PFS_DH2_HL24_ID20871_ii24_200&100_LDR/df_exp.rds")

Analysis.PFS <-  df.exp %>%
        mutate( EVENT = if_else(Tumor < 1.2 * TumorB, 0, 1),
                LAST=0) %>%
        group_by(ID) %>%
         # Identify the first DAY where EVENT = 1 for each ID
         mutate(first_event_day = ifelse(EVENT == 1, DAY, NA_real_)) %>%
         mutate(first_event_day = min(first_event_day, na.rm = TRUE)) %>%
         # Keep all rows where EVENT = 0 or it's the first occurrence of EVENT = 1
         filter((EVENT == 0 & DAY < first_event_day) | (EVENT == 1 & DAY == first_event_day)) %>%
         mutate(last_day = max(DAY))%>%
         mutate(LAST = if_else(DAY == last_day | EVENT == 1, 1, LAST)) %>%
         ungroup()%>%
         select(-first_event_day,-last_day)%>% filter(LAST == 1)%>%
         select(ID, DAY, EVENT)%>% rename(PFS=DAY, PFS.EVENT=EVENT)


df.exp.PFStruncation <- data.frame()

for (i in 1:1000) {
  single <- Analysis.PFS$PFS[i]
  rows_for_id <- df.exp[df.exp$ID == i, ]
  rows_for_id <- rows_for_id[rows_for_id$DAY <= single, ]
  max_row <- which.max(rows_for_id$DAY)
  rows_for_id$LAST <- ifelse(1:nrow(rows_for_id) == max_row, 1, 0)
  df.exp.PFStruncation <- bind_rows(df.exp.PFStruncation, rows_for_id)
}


df.ER <- df.exp.PFStruncation %>%
        group_by(ID) %>%
  
        mutate( EVENT = if_else(Tumor < 0.7 * TumorB, 1, 0),
                LAST=0) %>%
        group_by(ID) %>%
         # Identify the first DAY where EVENT = 1 for each ID
         mutate(first_event_day = ifelse(EVENT == 1, DAY, NA_real_)) %>%
         mutate(first_event_day = min(first_event_day, na.rm = TRUE)) %>%
         # Keep all rows where EVENT = 0 or it's the first occurrence of EVENT = 1
         filter((EVENT == 0 & DAY < first_event_day) | (EVENT == 1 & DAY == first_event_day)) %>%
         mutate(last_day = max(DAY))%>%
         mutate(LAST = if_else(DAY == last_day | EVENT == 1, 1, LAST)) %>%
         ungroup()%>%
         select(-first_event_day,-last_day)

analysis <- df.ER %>% filter(LAST == 1)

# Analysis.ORR <- analysis%>%select(ID, DAY, EVENT)%>% rename(ORR=DAY, ORR.EVENT=EVENT)
# combined_time <- left_join(Analysis.PFS, Analysis.ORR, by="ID")%>% mutate(Dif = PFS - ORR)
```


```{r}
KM_nOstrata_ORR <- survfit(Surv(DAY, EVENT) ~ 1,  data = analysis)

plot1_ORR<- KM_plot(KM_nOstrata_ORR, analysis, "ORR with treatment", 600,
       "C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/KM_PKPD model_ORR.tiff")
plot1_ORR

# Only contains responsors's data
ROD_PKPD_linear <-  df.exp %>%
                      select(ID, DAY, TumorB, Tumor)%>%
                      mutate( ORR = if_else(Tumor < 0.7 * TumorB, 1, 0))%>%
                      filter(ORR==1)%>%
                      group_by(ID) %>%
                      summarize(First_Response_Day = min(DAY),
                                Last_Response_Day = max(DAY)) %>%
                      filter(!is.infinite(First_Response_Day))%>%
                      mutate(DAY=Last_Response_Day-First_Response_Day,
                             EVENT=ifelse(DAY==600,0,1))%>%
                      arrange(DAY)
                     
KM_PKPD_DOR <- survfit(Surv(DAY, EVENT) ~ 1,  data = ROD_PKPD_linear)

Plot_PKPD_DOR<- KM_plot(KM_PKPD_DOR, ROD_PKPD_linear, "Tumor growth_DOR", 600,
       "C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/KM_PKPD_DOR.tiff")
Plot_PKPD_DOR

#generate the ORR summary workbook
row_names <- c("Min.", "1st Qu.", "Median", "Mean", "3rd Qu.", "Max.")

ORR_summary <- analysis %>%
              select(ID,DAY,DOSE,avgDOSE,CL,CP,Cmax, Ctrough,Cavg,CavgTE,TumorB,Kgrow, kdecay, EMAX,EC50, Ktol, Tumor,EVENT)%>%
              summarise(across(everything(), ~ summary(.x)))
rownames(ORR_summary) <- row_names
ORR_summary <- ORR_summary %>% rownames_to_column(var = "Statistic")%>%
              mutate(across(-Statistic, ~ if(is.numeric(.)) {
                    ifelse(. %% 1 == 0, as.integer(.), round(., 2))
                   } else {
                           .
                    }))

ORR.Event <-  analysis %>%filter(EVENT==1)
ORR_summary_event <- ORR.Event%>%
              select(ID,DAY,DOSE,avgDOSE,CL,CP,Cmax, Ctrough,Cavg,CavgTE,TumorB,Kgrow, kdecay, EMAX,EC50, Ktol, Tumor,EVENT)%>% 
              summarise(across(everything(), ~ summary(.x)))
rownames(ORR_summary_event) <- row_names
ORR_summary_event <- ORR_summary_event %>% rownames_to_column(var = "Statistic")%>%
                  mutate(across(-Statistic, ~ if(is.numeric(.)) {
                    ifelse(. %% 1 == 0, as.integer(.), round(., 2))
                   } else {
                           .
                    }))

ORR.noEvent <-  analysis %>%filter(EVENT!=1)
ORR_summary_noevent <- ORR.noEvent %>% 
                   select(ID,DAY,DOSE,avgDOSE,CL,CP,Cmax, Ctrough,Cavg,CavgTE,TumorB,Kgrow, kdecay, EMAX,EC50, Ktol, Tumor,EVENT)%>% 
                  summarise(across(everything(), ~ summary(.x)))
rownames(ORR_summary_noevent) <- row_names
ORR_summary_noevent <- ORR_summary_noevent %>% rownames_to_column(var = "Statistic")%>%
                  mutate(across(-Statistic, ~ if(is.numeric(.)) {
                    ifelse(. %% 1 == 0, as.integer(.), round(., 2))
                   } else {
                           .
                    }))

wb_ORR <- createWorkbook()
addWorksheet(wb_ORR, "ORR Summary")
addWorksheet(wb_ORR, "ORR Summary_event")
addWorksheet(wb_ORR, "ORR Summary_noevent")

writeData(wb_ORR, sheet = "ORR Summary", x = ORR_summary)
writeData(wb_ORR, sheet = "ORR Summary_event", x = ORR_summary_event)
writeData(wb_ORR, sheet = "ORR Summary_noevent", x = ORR_summary_noevent)

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR")
saveWorkbook(wb_ORR, file = "ORR Summary.xlsx", overwrite = TRUE)

#generate the typical Dose vs event for IDs having ORR
ORR.12IDs <- sample(ORR.Event$ID, 12)

ORR_duration_O <- ORR_duration%>% filter(ID %in% ORR.12IDs)
PFS.time_O <- PFS.time%>%filter(ID %in% ORR.12IDs)
ORR_Tumor_dose_plots <- lapply(ORR.12IDs, Tumor_Dose_plot, data = df.exp, response_duration = ORR_duration_O, pfs_linear = PFS.time_O)
ORR_combined_Tumor_dose_plot <- wrap_plots(ORR_Tumor_dose_plots, ncol = 3)

ggsave("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/Typical Tumor dose plot_ORR.tiff",
        plot = ORR_combined_Tumor_dose_plot,
         width = 12, height = 10, dpi = 400, units = "in")
 
```

#4 Conventional ER analysis 

NOTE: 
Cavg: daily average concentration; Cavg1D: Cavg on first day
Cavg1WC1: the average concentration in the first doing cycle(1w) equals to conc at the end of the first dosing cycle.
CavgTE2WC1:similar to the Cavg1WC1, the dosing cycle is 2W.
## 4.1 Prepare the df.ER.IDQ dataset 
```{r}
# first day exposure
df.ER.ID <- df.ER %>%
            filter(DAY == 1) %>%
            select(ID,CL,TumorB,Kgrow,kdecay,EMAX,EC50,Ktol,Ctrough,Cavg,Cavg2WC1,Cavg4WC1)%>%
            rename(Ctrough1D=Ctrough,
                   Cavg1D=Cavg)
# last day CavgTE and EVENT & DAY
G.ID <-  analysis[,c("ID","DOSE","DAY","avgDOSE","Ctrough", "Cavg","Cavg1W","Cavg2W","Cavg4W","Cavg2WC1","Cavg4WC1","CavgTE", "CavgTE2WC1","CavgTE4WC1","EVENT")]%>%
         rename(avgDoseTE=avgDOSE,
                CtroughOED=Ctrough,
                CavgOED=Cavg,
                Cavg1WOED=Cavg1W,
                Cavg2WOED=Cavg2W,
                Cavg4WOED=Cavg4W,
                Cavg2WC1OED=Cavg2WC1,
                Cavg4WC1OED=Cavg4WC1)

df.ER.IDQ <- merge(df.ER.ID, G.ID, by = "ID")%>%
             select(ID, DAY, DOSE, EVENT,avgDoseTE, CL, TumorB,Kgrow, kdecay, EMAX, EC50, Ktol, 
                    Ctrough1D, CtroughOED, Cavg1D,CavgOED,Cavg1WOED,
                    Cavg2WC1,Cavg2WOED,Cavg2WC1OED,
                    Cavg4WC1,Cavg4WOED,Cavg4WC1OED,
                    CavgTE,CavgTE2WC1,CavgTE4WC1)

```
## 4.2 KM plot(not necessary)
```{r}
Group <- 3

if(Group == 4) {
   legend.labels_Q <-c("Q1: 0-0.25", "Q2: 0.25-0.5", "Q3: 0.5-0.75", "Q4: 0.75-1")
   colors_Q <-c("red", "limegreen", "turquoise3", "blue2")

   #PK
  df.ER.IDQ$CL_IDQ  <- quantiles(df.ER.IDQ, "CL")
  df.ER.IDQ$Ctrough1D_IDQ  <- quantiles(df.ER.IDQ, "Ctrough1D")
  df.ER.IDQ$CtroughOED_IDQ  <- quantiles(df.ER.IDQ, "CtroughOED")

  df.ER.IDQ$Cavg1D_IDQ  <- quantiles(df.ER.IDQ, "Cavg1D")
  df.ER.IDQ$Cavg2WC1_IDQ  <- quantiles(df.ER.IDQ, "Cavg2WC1")
  df.ER.IDQ$Cavg4WC1_IDQ  <- quantiles(df.ER.IDQ, "Cavg4WC1")


  df.ER.IDQ$CavgOED_IDQ  <- quantiles(df.ER.IDQ, "CavgOED")
  df.ER.IDQ$Cavg1WOED_IDQ  <- quantiles(df.ER.IDQ, "Cavg1WOED")
  df.ER.IDQ$Cavg2WOED_IDQ  <- quantiles(df.ER.IDQ, "Cavg2WOED")
  df.ER.IDQ$Cavg4WOED_IDQ  <- quantiles(df.ER.IDQ, "Cavg4WOED")
  df.ER.IDQ$Cavg2WC1OED_IDQ  <- quantiles(df.ER.IDQ, "Cavg2WC1OED")
  df.ER.IDQ$Cavg4WC1OED_IDQ  <- quantiles(df.ER.IDQ, "Cavg4WC1OED")

  df.ER.IDQ$CavgTE_IDQ  <- quantiles(df.ER.IDQ, "CavgTE")
  df.ER.IDQ$CavgTE2WC1_IDQ  <- quantiles(df.ER.IDQ, "CavgTE2WC1")
  df.ER.IDQ$CavgTE4WC1_IDQ  <- quantiles(df.ER.IDQ, "CavgTE4WC1")

    } else  {
   legend.labels_Q <-c("Tertile1: 0-1/3", "Tertile2: 1/3-2/3", "Tertile3: 2/3-1")
   colors_Q <-c("red", "limegreen", "blue2")  
   

   #PK
  df.ER.IDQ$CL_IDQ  <- tertile(df.ER.IDQ, "CL")
  df.ER.IDQ$Ctrough1D_IDQ  <- tertile(df.ER.IDQ, "Ctrough1D")
  df.ER.IDQ$CtroughOED_IDQ  <- tertile(df.ER.IDQ, "CtroughOED")
  
  df.ER.IDQ$Cavg1D_IDQ  <- tertile(df.ER.IDQ, "Cavg1D")
  df.ER.IDQ$Cavg2WC1_IDQ  <- tertile(df.ER.IDQ, "Cavg2WC1")
  df.ER.IDQ$Cavg4WC1_IDQ  <- tertile(df.ER.IDQ, "Cavg4WC1")

  df.ER.IDQ$CavgOED_IDQ  <- tertile(df.ER.IDQ, "CavgOED")
  df.ER.IDQ$Cavg1WOED_IDQ  <- tertile(df.ER.IDQ, "Cavg1WOED")
  df.ER.IDQ$Cavg2WOED_IDQ  <- tertile(df.ER.IDQ, "Cavg2WOED")
  df.ER.IDQ$Cavg4WOED_IDQ  <- tertile(df.ER.IDQ, "Cavg4WOED")
  df.ER.IDQ$Cavg2WC1OED_IDQ  <- tertile(df.ER.IDQ, "Cavg2WC1OED")
  df.ER.IDQ$Cavg4WC1OED_IDQ  <- tertile(df.ER.IDQ, "Cavg4WC1OED")

  df.ER.IDQ$CavgTE_IDQ  <- tertile(df.ER.IDQ, "CavgTE")
  df.ER.IDQ$CavgTE2WC1_IDQ  <- tertile(df.ER.IDQ, "CavgTE2WC1")
  df.ER.IDQ$CavgTE4WC1_IDQ  <- tertile(df.ER.IDQ, "CavgTE4WC1")
 }  

#PK
  KM.CLIDQ <- survfit(Surv(DAY, EVENT) ~ CL_IDQ, data = df.ER.IDQ )
  KM.Ctrough1DIDQ <- survfit(Surv(DAY, EVENT) ~ Ctrough1D_IDQ, data = df.ER.IDQ )
  KM.CtroughOEDIDQ <- survfit(Surv(DAY, EVENT) ~ CtroughOED_IDQ, data = df.ER.IDQ )
  
  KM.Cavg1DIDQ <- survfit(Surv(DAY, EVENT) ~ Cavg1D_IDQ, data = df.ER.IDQ )
  KM.Cavg2WC1IDQ <- survfit(Surv(DAY, EVENT) ~ Cavg2WC1_IDQ, data = df.ER.IDQ )
  KM.Cavg4WC1IDQ <- survfit(Surv(DAY, EVENT) ~ Cavg4WC1_IDQ, data = df.ER.IDQ )

  KM.CavgOEDIDQ <- survfit(Surv(DAY, EVENT) ~ CavgOED_IDQ, data = df.ER.IDQ)
  KM.Cavg1WOEDIDQ <- survfit(Surv(DAY, EVENT) ~ Cavg1WOED_IDQ, data = df.ER.IDQ )
  KM.Cavg2WOEDIDQ <- survfit(Surv(DAY, EVENT) ~ Cavg2WOED_IDQ, data = df.ER.IDQ )
  KM.Cavg4WOEDIDQ <- survfit(Surv(DAY, EVENT) ~ Cavg4WOED_IDQ, data = df.ER.IDQ )
  KM.Cavg2WC1OEDIDQ <- survfit(Surv(DAY, EVENT) ~ Cavg2WC1OED_IDQ, data = df.ER.IDQ )
  KM.Cavg4WC1OEDIDQ <- survfit(Surv(DAY, EVENT) ~ Cavg4WC1OED_IDQ, data = df.ER.IDQ )

  KM.CavgTEIDQ <- survfit(Surv(DAY, EVENT) ~ CavgTE_IDQ, data = df.ER.IDQ )
  KM.CavgTE2WC1IDQ <- survfit(Surv(DAY, EVENT) ~ CavgTE2WC1_IDQ, data = df.ER.IDQ )
  KM.CavgTE4WC1IDQ <- survfit(Surv(DAY, EVENT) ~ CavgTE4WC1_IDQ, data = df.ER.IDQ )
  
plot.CL <- KM_plot_Q(KM.CLIDQ, df.ER.IDQ,"CL_IDQ",legend.labels_Q, colors_Q,600,
       "C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/KM_ORR_DH2_CL.tiff")

# if (DI == 1) {
KMplot.PK1 <- KM_plot_G(KM.Ctrough1DIDQ, df.ER.IDQ,"Ctrough1D_IDQ",legend.labels_Q, colors_Q,600,
       "C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/KM_ORR_DH2_Ctrough1D.tiff")
KMplot.PK2 <- KM_plot_G(KM.Cavg1DIDQ, df.ER.IDQ,"Cavg1D_IDQ",legend.labels_Q, colors_Q,600,
       "C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/KM_ORR_DH2_Cavg1D.tiff")


KMplot.PK3 <- KM_plot_G(KM.Cavg1WOEDIDQ, df.ER.IDQ,"Cavg1WOED_IDQ",legend.labels_Q, colors_Q,600,
       "C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/KM_ORR_DH2_Cavg1WOED.tiff")
KMplot.PK4 <-KM_plot_G(KM.Cavg2WOEDIDQ, df.ER.IDQ,"Cavg2WOED_IDQ",legend.labels_Q, colors_Q,600,
       "C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/KM_ORR_DH2_Cavg2WOED.tiff")
KMplot.PK5 <-KM_plot_G(KM.Cavg4WOEDIDQ, df.ER.IDQ,"Cavg4WOED_IDQ",legend.labels_Q, colors_Q,600,
       "C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/KM_ORR_DH2_Cavg4WOED.tiff")
KMplot.PK6 <- KM_plot_G(KM.CavgTEIDQ, df.ER.IDQ,"CavgTE_IDQ",legend.labels_Q, colors_Q,600,
       "C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/KM_ORR_DH2_CavgTE.tiff")

KMplot.combined.PK <- grid.arrange(KMplot.PK1$plot, KMplot.PK2$plot, KMplot.PK3$plot, KMplot.PK4$plot,KMplot.PK5$plot, KMplot.PK6$plot, ncol = 3)

ggsave("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/KM_ORR_DH2_PK.tiff",
      plot = KMplot.combined.PK, 
     width = 15, height = 8, dpi = 400, units = "in") 

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR")
write.csv(df.ER.IDQ, "df_ER_IDQ.csv", row.names = FALSE)
```
## 4.3 Conventional ER analysis

```{r}
setwd( "C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR") 
df.ER.IDQ <- read.csv("df_ER_IDQ.csv")
#1. Perform Wilcox Test for the exposures grouped by IDs 
## get the mean values for the exposures
ID.e <- df.ER.IDQ %>% filter(EVENT==1)
ID.n <- df.ER.IDQ %>% filter(EVENT==0)

covariates <- colnames(df.ER.IDQ)[c(5:26)]
wilcox_result <- wilcox(ID.e, ID.n, covariates)%>%rownames_to_column(var = "Variable")

#2. univariate Cox PH regression_continuous covariate
univ_formulas <- sapply(covariates, function(x) as.formula(paste('Surv(DAY, EVENT) ~', x)))
univ_models <- lapply(univ_formulas, function(x) { coxph(x, data = df.ER.IDQ) })
univ_con_result <- univ_con(univ_models)%>%
                   as.data.frame() %>%
                  rownames_to_column(var = "Variable")

#3. logistic regression analysis

logistic_formulas <- sapply(covariates, function(x) as.formula(paste('EVENT ~', x)))
logistic_Results <- lapply(logistic_formulas, function(x) glm(x, family = binomial(logit), data = df.ER.IDQ))
logistic_result  <- logistic_analysis(logistic_Results,covariates)%>% 
                    rownames_to_column(var = "Variable")


wb <- createWorkbook()
addWorksheet(wb, "Logistic Result")
addWorksheet(wb, "CoxPH Conc Result")
addWorksheet(wb, "wilcox result")

writeData(wb, sheet = "Logistic Result", x = logistic_result)
writeData(wb, sheet = "CoxPH Conc Result", x = univ_con_result)
writeData(wb, sheet = "wilcox result", x = wilcox_result)

# abstract the results
variables_to_abstract <- colnames(df.ER.IDQ)[c(5,6,7,10,11,13:17,19,22,24)]
logistic_result_abstract <- logistic_result %>% filter (Variable%in% variables_to_abstract)
CoxPH_conc_abstract <- univ_con_result %>% filter (Variable%in% variables_to_abstract)%>% select(Variable,beta,P.Value)

wb_abstract <- createWorkbook()
addWorksheet(wb_abstract, "Logistic Result Abstract")
addWorksheet(wb_abstract, "CoxPH Conc Abstract")
writeData(wb_abstract, sheet = "Logistic Result Abstract", x = logistic_result_abstract)
writeData(wb_abstract, sheet = "CoxPH Conc Abstract", x = CoxPH_conc_abstract)

setwd( "C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR") 
saveWorkbook(wb, file = "Conventional ER methods result.xlsx", overwrite = TRUE)
saveWorkbook(wb_abstract, file = "CoxPH&logistic abstract result.xlsx", overwrite = TRUE)
```

##4.4 Logistic plot(General linear model)
### summary results
Set DOSE=0.01 if DOSE is 0, assuming that dose of 0 and 0.01 have same ER responses
```{r}
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR")
df.ER.IDQ <- read.csv("df_ER_IDQ.csv")

#generate the logistic summary workbook
row_names <- c("Min.", "1st Qu.", "Median", "Mean", "3rd Qu.", "Max.")

LG_ORR_summary <- df.ER.IDQ  %>%
              select(ID,DAY,EVENT,DOSE,avgDoseTE,Ctrough1D, Cavg1D, CtroughOED, CavgOED,Cavg1WOED,Cavg2WOED,CavgTE,CL,TumorB,EMAX, EC50)%>%
              summarise(across(everything(), ~ summary(.x)))
rownames(LG_ORR_summary) <- row_names
LG_ORR_summary <- LG_ORR_summary %>% rownames_to_column(var = "Statistic")%>%
                 mutate(across(-Statistic, ~ if(is.numeric(.)) {
                    ifelse(. %% 1 == 0, as.integer(.), round(., 2))
                   } else {
                           .
                    }))

LG_ORR.Event <-  df.ER.IDQ  %>%filter(EVENT==1)
LG_ORR_summary_event <- LG_ORR.Event%>%
              select(ID,DAY,EVENT,DOSE,avgDoseTE,Ctrough1D, Cavg1D, CtroughOED, CavgOED,Cavg1WOED,Cavg2WOED,CavgTE,CL,TumorB,EMAX, EC50)%>%
              summarise(across(everything(), ~ summary(.x)))
rownames(LG_ORR_summary_event) <- row_names
LG_ORR_summary_event <- LG_ORR_summary_event %>% rownames_to_column(var = "Statistic")%>%
                 mutate(across(-Statistic, ~ if(is.numeric(.)) {
                    ifelse(. %% 1 == 0, as.integer(.), round(., 2))
                   } else {
                           .
                    }))

LG_ORR.noEvent <-  df.ER.IDQ  %>%filter(EVENT!=1)
LG_ORR_summary_noevent <- LG_ORR.noEvent %>% 
                select(ID,DAY,EVENT,DOSE,avgDoseTE,Ctrough1D,Cavg1D, CtroughOED, CavgOED,Cavg1WOED,Cavg2WOED,CavgTE,CL,TumorB,EMAX, EC50)%>%
                  summarise(across(everything(), ~ summary(.x)))
rownames(LG_ORR_summary_noevent) <- row_names
LG_ORR_summary_noevent <- LG_ORR_summary_noevent %>% rownames_to_column(var = "Statistic")%>%
                  mutate(across(-Statistic, ~ if(is.numeric(.)) {
                    ifelse(. %% 1 == 0, as.integer(.), round(., 2))
                   } else {
                           .
                    }))

LG_wb_ORR <- createWorkbook()
addWorksheet(LG_wb_ORR, "ORR Summary")
addWorksheet(LG_wb_ORR, "ORR Summary_event")
addWorksheet(LG_wb_ORR, "ORR Summary_noevent")

writeData(LG_wb_ORR, sheet = "ORR Summary", x = LG_ORR_summary)
writeData(LG_wb_ORR, sheet = "ORR Summary_event", x = LG_ORR_summary_event)
writeData(LG_wb_ORR, sheet = "ORR Summary_noevent", x = LG_ORR_summary_noevent)

predictor <- c("DOSE", "avgDoseTE","Ctrough1D","Cavg1D","CtroughOED",
               "CavgOED","Cavg1WOED","Cavg2WOED","Cavg4WOED","CavgTE")

EC50_output <- Calculate_EC50_linear(predictor, df.ER.IDQ)

# Save the workbook to an Excel file
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR")
saveWorkbook(LG_wb_ORR, file = "ORR Summary of logistic regression.xlsx", overwrite = TRUE)
write.csv(EC50_output, "EC50_results_linear.csv", row.names = TRUE)
```
### genetate plots_consider log transformation the exposure metrics
```{r}
logistic_regression_comparison <- function(df.ER.IDQ, TRUE_DH1, TRUE_DH2, x_var, y_var) {
  # Ensure x variable is numeric for log scale
 
  ggplot() +
  
     # Logistic regression line for current dataset
    geom_smooth(data = df.ER.IDQ, aes(x = .data[[x_var]], y = .data[[y_var]], color = "Logistic Regression"), 
                method = "glm", method.args = list(family = "binomial")) +
    geom_point(data = df.ER.IDQ, aes(x = .data[[x_var]], y = .data[[y_var]]), 
               shape = "|", alpha = 0.5) +
    
      # Original True ER line for DH2
    geom_line(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH2"), size = 1.5) +
    geom_point(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH2"), size = 2) +
    geom_text(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], label = DOSE, color = "True ER_DH2"), 
              vjust = 0.8, hjust = -0.4,angle = -50, size = 3.5) +
    
    # Original True ER line for DH1
    geom_line(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH1"), size = 1.5) +
    geom_point(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH1"), size = 2) +
    geom_text(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], label = DOSE), 
              vjust = 0.2, hjust = -0.4,angle = 75, size = 3.5) +
    
    custom_theme +
    theme(
      panel.background = element_rect(fill = "white", color = "black"),
      legend.background = element_rect(fill = "transparent"),
      legend.position = c(0.3, 0.8),
      legend.title = element_blank(),
      axis.text.x = element_text(size = 12, angle = 0, hjust = 1),
      axis.text.y = element_text(size = 12),
      axis.title = element_text(size = 12),
      plot.title = element_text(size = 14, hjust = 0.5),
      plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm")
        ) +
    labs(
      x = x_var,
      y = "Probability of ORR Event",
      title = paste("Logistic Regression -", x_var),
      color = "Model"
    ) +
   coord_cartesian(ylim = c(0, 1), xlim = c(0.1, NA))+
    scale_y_continuous(breaks = seq(0, 1, 0.2)) +
    scale_x_log10(labels = custom_log_labels) +
    scale_color_manual(values = c("Logistic Regression" = "black","True ER_DH2" = "blue", "True ER_DH1" = "forestgreen"))
}

## compare the true ER for DH1 and DH2
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/True ER relationship/DH1")
ORR_trueER_DH1 <- read.csv("True ER_ORR.csv")
ORR_trueER_DH1$avgDoseTE <- ORR_trueER_DH1$DOSE

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/True ER relationship/DH2_LDR_method3")
ORR_trueER_DH2 <- read.csv("True ER_ORR_LDR_DH2.csv")

Logiplot1 <- logistic_regression_comparison(df.ER.IDQ, ORR_trueER_DH1, ORR_trueER_DH2, "avgDoseTE", "EVENT")
Logiplot2 <- logistic_regression_comparison(df.ER.IDQ, ORR_trueER_DH1, ORR_trueER_DH2, "Ctrough1D", "EVENT")
Logiplot3 <- logistic_regression_comparison(df.ER.IDQ, ORR_trueER_DH1, ORR_trueER_DH2, "Cavg1D", "EVENT")
Logiplot4 <- logistic_regression_comparison(df.ER.IDQ, ORR_trueER_DH1, ORR_trueER_DH2, "CtroughOED", "EVENT")
Logiplot5 <- logistic_regression_comparison(df.ER.IDQ, ORR_trueER_DH1, ORR_trueER_DH2, "CavgOED", "EVENT")
Logiplot6 <- logistic_regression_comparison(df.ER.IDQ, ORR_trueER_DH1, ORR_trueER_DH2, "Cavg1WOED", "EVENT")
Logiplot7 <- logistic_regression_comparison(df.ER.IDQ, ORR_trueER_DH1, ORR_trueER_DH2, "Cavg2WOED", "EVENT")
Logiplot8 <- logistic_regression_comparison(df.ER.IDQ, ORR_trueER_DH1, ORR_trueER_DH2, "CavgTE", "EVENT")

Logistic_comparison <- grid.arrange(Logiplot1, Logiplot2, Logiplot3, Logiplot4,Logiplot5,Logiplot6,Logiplot7, Logiplot8,ncol = 4)

ggsave("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/True ER comparions_DH1&2_ORR.tiff",
      plot = Logistic_comparison, 
     width = 20, height = 8, dpi = 400, units = "in")
```


## 4.5 logistic plot(Emax model_N=1) with control group
```{r}
#input the true ER relationship dataset
# setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/True ER relationship/DH1")
# ORR_trueER_DH1 <- read.csv("True ER_ORR.csv")
# ORR_trueER_DH1$avgDoseTE <- ORR_trueER_DH1$DOSE
# 
# setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/True ER relationship/DH2_LDR_method3")
# ORR_trueER_DH2 <- read.csv("True ER_ORR_LDR_DH2.csv")
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR")
df.ER.IDQ <- read.csv("df_ER_IDQ.csv")


setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis")
df.ER.IDQ.Control <- read.csv("df_ER_IDQ_ORR_NOTreatment.csv")
df.ER.IDQ.Control$DOSE_IDQ  <- 0
merged_df.ER.IDQ <- bind_rows(df.ER.IDQ.Control, df.ER.IDQ)
merged_df.ER.IDQ$avgDoseTE  <- 0


random_seed <- 2024
set.seed(random_seed)

covariates <- c( "Ctrough1D", "Cavg1D", "CtroughOED", "CavgOED", "Cavg1WOED","CavgTE")
# covariates <- c("Cavg1D")

 wb <- createWorkbook()

# Loop through each covariate
for (cov in covariates) {
  
  # Define y_var based on covariate
   y_var <- "EVENT"
  
  # Update the model formula
  model <- bf(
    as.formula(paste("EVENT ~ E0 + Emax *", cov, "/ (EC50 +", cov, ")")),
    E0 + Emax + EC50 ~ 1,
    nl = TRUE
  )

  # Define the priors
  p <- prior(normal(10, 5), nlpar = "E0") +
       prior(normal(50, 25), nlpar = "Emax") +
       prior(normal(75, 50), nlpar = "EC50", lb = 0) 
      
  # Fit the model############Change data#########################
  fit <- brm(
    model,
    prior = p,
    data = merged_df.ER.IDQ,
    cores = 4,
    control = list(adapt_delta = .99)
  )

  # Create a sequence of x-values on a log scale
  x_values <- seq(0.1, max(merged_df.ER.IDQ[[cov]]), by = 1)
  newdata <- setNames(data.frame(x_values), cov)

# posterior_epred gives expected values
predictions <- posterior_epred(fit, newdata = newdata)

# You can summarize the predictions (e.g., mean and credible intervals)
summary_pred <- apply(predictions, 2, function(x) {
  c(mean = mean(x), lower = quantile(x, 0.025), upper = quantile(x, 0.975))
})

summary_pred_df <- data.frame(
  x_values = x_values,
  mean = summary_pred["mean", ],
  lower = summary_pred["lower.2.5%", ],
  upper = summary_pred["upper.97.5%", ]
)
names(summary_pred_df)[names(summary_pred_df) == "lower.2.5%"] <- "lower"
names(summary_pred_df)[names(summary_pred_df) == "upper.97.5%"] <- "upper"
  
  
    # Create the plot object with all customizations
  plot_obj <- ggplot(summary_pred_df, aes(x = x_values, y =  mean, color="Logistic Regression")) +
    geom_line(size = 1) +
   geom_ribbon(aes(ymin =  lower, ymax =  upper), alpha = 0.2, fill = "black") +
   
        # Adding the True ER lines for DH2
    geom_line(data = ORR_trueER_DH2, aes(x = .data[[cov]], y = .data[[y_var]], color = "True ER_DH2"), size = 1.5) +
    geom_point(data = ORR_trueER_DH2, aes(x = .data[[cov]], y = .data[[y_var]], color = "True ER_DH2"), size = 2) +
    geom_text(data = ORR_trueER_DH2, aes(x = .data[[cov]], y = .data[[y_var]], label = DOSE, color = "True ER_DH2"), 
              vjust = 0.8, hjust = -0.4, angle = -50, size = 3.5) +
    
    # Adding the True ER lines for DH1
    geom_line(data = ORR_trueER_DH1, aes(x = .data[[cov]], y = .data[[y_var]], color = "True ER_DH1"), size = 1.5) +
    geom_point(data = ORR_trueER_DH1, aes(x = .data[[cov]], y = .data[[y_var]], color = "True ER_DH1"), size = 2) +
    geom_text(data = ORR_trueER_DH1, aes(x = .data[[cov]], y = .data[[y_var]], label = DOSE, color = "True ER_DH1"), 
              vjust = 0.2, hjust = -0.4, angle = 75, size = 3.5) +
    custom_theme +
      theme(
      panel.background = element_rect(fill = "white", color = "black"),
      legend.background = element_rect(fill = "transparent"),
      legend.position = c(0.3, 0.8),
      legend.title = element_blank(),
      axis.text.x = element_text(size = 12, angle = 0, hjust = 1),
      axis.text.y = element_text(size = 12),
      axis.title = element_text(size = 12),
      plot.title = element_text(size = 14, hjust = 0.5),
      plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm")
        ) +
    labs(x = cov, 
         y = "Probability of ORR Event",
        title = paste("Logistic Regression(Emax) -", cov)) +
    scale_y_continuous(breaks = seq(0, 1, 0.2)) +
    coord_cartesian(ylim = c(0, 1), xlim = c(0.1, NA))+
    scale_x_log10(labels = custom_log_labels) +
    scale_color_manual(values = c("Logistic Regression" = "black","True ER_DH2" = "blue", "True ER_DH1" = "forestgreen"))

  # Save the plot as a TIFF file
  plot_file_name <- paste0(cov, ".tiff")
  setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/Emax_withcontrol_correct")
  ggsave(plot_file_name, plot = plot_obj, width = 5, height = 4, dpi = 400)
  
   saveRDS(fit, file = paste0("fit_", cov, ".rds"))
  # Extract and save regression coefficients to Excel
  coeffs <- as.data.frame(fixef(fit))  # Extract fixed effects coefficients
  coeffs <- cbind(Parameter = rownames(coeffs), coeffs)  # Add a column for parameter names
  rownames(coeffs) <- NULL  # Remove row names
  addWorksheet(wb, cov)
  writeData(wb, sheet = cov, coeffs)
}

# Save the Excel workbook
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/Emax_withcontrol_correct")
saveWorkbook(wb, "regression_coefficients.xlsx", overwrite = TRUE)

```

### Adjust the plots if need
```{r}
## read the data
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/Emax")

ce <- readRDS("ce_Cavg1D.rds")
cov <- "Cavg1D"

# ce <- readRDS("ce_Ctrough1D.rds")
# cov <- "Ctrough1D"

# ce <- readRDS("ce_CavgSS.rds")
# cov <- "CavgSS"

# ce <- readRDS("ce_CtroughOED.rds")
# cov <- "CtroughOED"
# 
# ce <- readRDS("ce_CavgOED.rds")
# cov <- "CavgOED"
# 
# ce <- readRDS("ce_Cavg1WOED.rds")
# cov <- "Cavg1WOED"
# 
# ce <- readRDS("ce_Cavg2WOED.rds")
# cov <- "Cavg2WOED"
# 
# ce <- readRDS("ce_CavgTE.rds")
# cov <- "CavgTE"

y_var <- "EVENT"

 # Create a sequence of x-values on a log scale
x_values <- seq(0.1, max(cov), by = 0.1, scale = "log")
  
  # Get predicted values and confidence intervals
  predictions <- data.frame(
    Covariate = x_values,
    Predicted_Prob = plogis(predict(fit, newdata = data.frame(cov = x_values), allow_new_levels = TRUE)$Estimate),
    Lower_Bound = plogis(predict(fit, newdata = data.frame(cov = x_values), allow_new_levels = TRUE)$Lower),
    Upper_Bound = plogis(predict(fit, newdata = data.frame(cov = x_values), allow_new_levels = TRUE)$Upper)
   )
  
ce_data <- ce[[1]]


 plot_obj <- ggplot(ce_data, aes(x = .data[[cov]], y = estimate__, color="Logistic Regression")) +
    geom_line(size = 1) +
   geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.2, fill = "black") +
   
    # Adding the True ER lines for DH1
    geom_line(data = True.ER, aes(x = .data[[cov]], y = .data[[y_var]], color = "True ER_DH1"), size = 1.5) +
    geom_point(data = True.ER, aes(x = .data[[cov]], y = .data[[y_var]], color = "True ER_DH1"), size = 2) +
    geom_text(data = True.ER, aes(x = .data[[cov]], y = .data[[y_var]], label = DOSE, color = "True ER_DH1"), 
              vjust = 0.2, hjust = -0.4, angle = 75, size = 3.5) +
    custom_theme +
      theme(
      panel.background = element_rect(fill = "white", color = "black"),
      legend.background = element_rect(fill = "transparent"),
      legend.position = c(0.3, 0.8),
      legend.title = element_blank(),
      axis.text.x = element_text(size = 12, angle = 0, hjust = 1),
      axis.text.y = element_text(size = 12),
      axis.title = element_text(size = 12),
      plot.title = element_text(size = 14, hjust = 0.5),
      plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm")
        ) +
    labs(x = cov, 
         y = "Probability of ORR Event",
        title = paste("Logistic Regression(Emax) -", cov)) +
    scale_y_continuous(breaks = seq(0, 1, 0.2)) +
    coord_cartesian(ylim = c(0, 1), xlim = c(0.1, NA))+
    scale_x_log10(labels = custom_log_labels) +
    scale_color_manual(values = c("Logistic Regression" = "black", "True ER_DH1" = "forestgreen"))

  # Save the plot as a TIFF file
  plot_file_name <- paste0(cov, ".tiff")
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR/True Positive ER_ORR_DH1_HL24_ID20871_ii24_10mg/Emax")
  ggsave(plot_file_name, plot = plot_obj, width = 5, height = 4, dpi = 400)

```

### Get the comparison results across the different dose combinations
```{r}
### Get the comparison results across the different dose combinations
Abstract_EC50 <- function(path, file_name, dose_variable) {
  setwd(path)
  file_path <- file_name
  sheet_names <- excel_sheets(file_path)
  results <- list()
  
  # Loop through each sheet and extract the relevant row
  for (sheet in sheet_names) {
    data <- read_excel(file_path, sheet = sheet)
    extracted_row <- data %>%
      filter(Parameter == "EC50_Intercept")
    
    # Add the sheet name as a column
    if (nrow(extracted_row) > 0) {
      extracted_row <- extracted_row %>%
        mutate(Covariates = sheet)
    
      # Append the result to the list
      results[[sheet]] <- extracted_row
    }
  }
  
  # Combine all extracted rows into one data frame
  final_result <- bind_rows(results)
  
  # Select relevant columns
  final_result <- final_result %>% select(Parameter, Covariates, Estimate, Est.Error, Q2.5, Q97.5)%>%
  mutate(across(c(Estimate, Est.Error, Q2.5, Q97.5), ~ round(.x, 2)))
  # Assign the result to a variable with the name given in dose_variable
  assign(dose_variable, final_result, envir = .GlobalEnv)
}

Abstract_EC50("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/Emax_withcontrol_correct", "regression_coefficients.xlsx", "EC50_500")
Abstract_EC50("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/Emax_withcontrol_correct", "regression_coefficients.xlsx", "EC50_200")
Abstract_EC50("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/Emax_withcontrol_correct", "regression_coefficients.xlsx", "EC50_100")
Abstract_EC50("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/Emax_withcontrol_correct", "regression_coefficients.xlsx", "EC50_60")

wb_EC50 <- createWorkbook()
addWorksheet(wb_EC50, "200&60")
addWorksheet(wb_EC50, "200&100")
addWorksheet(wb_EC50, "500&100")
addWorksheet(wb_EC50, "200&100")
writeData(wb_EC50, sheet = "200&60", x = EC50_500)
writeData(wb_EC50, sheet = "200&100", x = EC50_200)
writeData(wb_EC50, sheet = "500&100", x = EC50_100)
writeData(wb_EC50, sheet = "200&100", x = EC50_60)
setwd( "C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation") 
saveWorkbook(wb_EC50, file = "Emax model_EC50_withcontrol.xlsx", overwrite = TRUE)

```

# 5. Validate the log transformation issue
### generate plots_2 did not consider log transformation
```{r}
#input the true ER relationship dataset
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/True ER relationship/DH1")
True.ER <- read.csv("True ER_ORR.csv")
True.ER$avgDoseTE <- True.ER$DOSE
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/True ER relationship/DH2_LDR_method3")
ORR_trueER_DH2 <- read.csv("True ER_ORR_LDR_DH2.csv")

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR")
df.ER.IDQ <- read.csv("df_ER_IDQ.csv")

## get the prediction results
covariates <- c("avgDoseTE", "Ctrough1D", "Cavg1D","CtroughOED", "CavgOED", "Cavg1WOED","Cavg2WOED" , "CavgTE")
logistic_formulas <- sapply(covariates, function(x) as.formula(paste('EVENT ~', x)))
logistic_Results_plot <- lapply(logistic_formulas, function(formula) {
  # Fit the model
  model <- glm(formula, family = binomial(logit), data = df.ER.IDQ)
  
  # Get predicted values on the scale of log-odds (link = "logit") and convert to probabilities
  predictions <- predict(model, type = "link", se.fit = TRUE)
  
  # Confidence intervals for predictions
  lower_bound <- predictions$fit - 1.96 * predictions$se.fit
  upper_bound <- predictions$fit + 1.96 * predictions$se.fit
  
  # Convert to probability scale
  predicted_prob <- plogis(predictions$fit)
  lower_prob <- plogis(lower_bound)
  upper_prob <- plogis(upper_bound)
  
  # Return a data frame with the covariate values, predictions, and confidence intervals
  data.frame(
    Covariate = df.ER.IDQ[[all.vars(formula)[2]]],  # Extract covariate values
    Predicted_Prob = predicted_prob,
    Lower_Bound = lower_prob,
    Upper_Bound = upper_prob
  )
})

wb <- createWorkbook()
for (i in seq_along(covariates)) {
  addWorksheet(wb, covariates[i])  # Create a sheet named after the covariate
  writeData(wb, sheet = covariates[i], logistic_Results_plot [[i]])  # Write the data frame to the sheet
}


# Save the workbook to a file
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR")
saveWorkbook(wb, "logistic_regression_results.xlsx", overwrite = TRUE)

logistic_regression_comparison <- function(df, TRUE_DH1, TRUE_DH2, x_var, y_var) {
  # Ensure x variable is numeric for log scale
 
  ggplot() +
  
     # Logistic regression line for current dataset
    geom_line(data = df, aes(x = Covariate, y = Predicted_Prob, color = "Logistic Regression"), size=1.5) +
    geom_ribbon(data = df, aes( x = Covariate, ymin = Lower_Bound, ymax = Upper_Bound), alpha = 0.2, fill = "black") +
    
      # Original True ER line for DH2
    geom_line(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH2"), size = 1.5) +
    geom_point(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH2"), size = 2) +
    geom_text(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], label = DOSE, color = "True ER_DH2"), 
              vjust = 0.8, hjust = -0.4,angle = -50, size = 3.5) +
    
    # Original True ER line for DH1
    geom_line(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH1"), size = 1.5) +
    geom_point(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH1"), size = 2) +
    geom_text(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], label = DOSE), 
              vjust = 0.2, hjust = -0.4,angle = 75, size = 3.5) +
    
    custom_theme +
    theme(
      panel.background = element_rect(fill = "white", color = "black"),
      legend.background = element_rect(fill = "transparent"),
      legend.position = c(0.3, 0.8),
      legend.title = element_blank(),
      axis.text.x = element_text(size = 12, angle = 0, hjust = 1),
      axis.text.y = element_text(size = 12),
      axis.title = element_text(size = 12),
      plot.title = element_text(size = 14, hjust = 0.5),
      plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm")
        ) +
    labs(
      x = x_var,
      y = "Probability of ORR Event",
      title = paste("Logistic Regression -", x_var),
      color = "Model"
    ) +
   coord_cartesian(ylim = c(0, 1), xlim = c(0.1, NA))+
    scale_y_continuous(breaks = seq(0, 1, 0.2)) +
    scale_x_log10(labels = custom_log_labels) +
    scale_color_manual(values = c("Logistic Regression" = "black","True ER_DH2" = "blue", "True ER_DH1" = "forestgreen"))
}

## compare the true ER for DH1 and DH2

Logiplot1 <- logistic_regression_comparison(logistic_Results_plot$avgDoseTE, True.ER, ORR_trueER_DH2, "avgDoseTE", "EVENT")
Logiplot2 <- logistic_regression_comparison(logistic_Results_plot$Ctrough1D, True.ER, ORR_trueER_DH2, "Ctrough1D", "EVENT")
Logiplot3 <- logistic_regression_comparison(logistic_Results_plot$Cavg1D, True.ER, ORR_trueER_DH2, "Cavg1D", "EVENT")
Logiplot4 <- logistic_regression_comparison(logistic_Results_plot$CtroughOED, True.ER, ORR_trueER_DH2, "CtroughOED", "EVENT")
Logiplot5 <- logistic_regression_comparison(logistic_Results_plot$CavgOED, True.ER, ORR_trueER_DH2, "CavgOED", "EVENT")
Logiplot6 <- logistic_regression_comparison(logistic_Results_plot$Cavg1WOED, True.ER, ORR_trueER_DH2, "Cavg1WOED", "EVENT")
Logiplot7 <- logistic_regression_comparison(logistic_Results_plot$Cavg2WOED, True.ER, ORR_trueER_DH2, "Cavg2WOED", "EVENT")
Logiplot8 <- logistic_regression_comparison(logistic_Results_plot$CavgTE, True.ER, ORR_trueER_DH2, "CavgTE", "EVENT")

# Logistic_comparison <- grid.arrange(Logiplot1, Logiplot2, Logiplot3, Logiplot4,Logiplot5,Logiplot6,Logiplot7, Logiplot8,ncol = 4)
Logistic_comparison <- grid.arrange(Logiplot2, Logiplot4, Logiplot6, Logiplot3, Logiplot5, Logiplot8,ncol = 3)

ggsave("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/True ER comparions_DH1&2_ORR_nolog.tiff",
      plot = Logistic_comparison, 
     width = 15, height = 8, dpi = 400, units = "in")

```
### generate plots_2  consider log transformation
```{r}
#input the true ER relationship dataset
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/True ER relationship/DH1")
True.ER <- read.csv("True ER_ORR.csv")
True.ER$avgDoseTE <- True.ER$DOSE
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/True ER relationship/DH2_LDR_method3")
ORR_trueER_DH2 <- read.csv("True ER_ORR_LDR_DH2.csv")

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR")
df.ER.IDQ <- read.csv("df_ER_IDQ.csv")

## get the prediction results
covariates <- c("Ctrough1D", "Cavg1D","CtroughOED", "CavgOED", "Cavg1WOED","Cavg2WOED" , "CavgTE")
logistic_formulas <- sapply(covariates, function(x) as.formula(paste('EVENT ~ log(', x, ')')))
logistic_Results_plot <- lapply(logistic_formulas, function(formula) {
  # Fit the model
  model <- glm(formula, family = binomial(logit), data = df.ER.IDQ)
  
  # Get predicted values on the scale of log-odds (link = "logit") and convert to probabilities
  predictions <- predict(model, type = "link", se.fit = TRUE)
  
  # Confidence intervals for predictions
  lower_bound <- predictions$fit - 1.96 * predictions$se.fit
  upper_bound <- predictions$fit + 1.96 * predictions$se.fit
  
  # Convert to probability scale
  predicted_prob <- plogis(predictions$fit)
  lower_prob <- plogis(lower_bound)
  upper_prob <- plogis(upper_bound)
  
  # Return a data frame with the covariate values, predictions, and confidence intervals
  data.frame(
    Covariate = df.ER.IDQ[[all.vars(formula)[2]]],  # Extract covariate values
    Predicted_Prob = predicted_prob,
    Lower_Bound = lower_prob,
    Upper_Bound = upper_prob
  )
})

wb <- createWorkbook()
for (i in seq_along(covariates)) {
  addWorksheet(wb, covariates[i])  # Create a sheet named after the covariate
  writeData(wb, sheet = covariates[i], logistic_Results_plot [[i]])  # Write the data frame to the sheet
}

summary(logistic_Results_plot)
# Save the workbook to a file
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR")
saveWorkbook(wb, "logistic_regression_results_test.xlsx", overwrite = TRUE)

logistic_regression_comparison <- function(df, TRUE_DH1, TRUE_DH2, x_var, y_var) {
  # Ensure x variable is numeric for log scale
 
  ggplot() +
  
     # Logistic regression line for current dataset
    geom_line(data = df, aes(x = Covariate, y = Predicted_Prob, color = "Logistic Regression"), size=1.5) +
    geom_ribbon(data = df, aes( x = Covariate, ymin = Lower_Bound, ymax = Upper_Bound), alpha = 0.2, fill = "black") +
    
      # Original True ER line for DH2
    geom_line(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH2"), size = 1.5) +
    geom_point(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH2"), size = 2) +
    geom_text(data = TRUE_DH2, aes(x = .data[[x_var]], y = .data[[y_var]], label = DOSE, color = "True ER_DH2"), 
              vjust = 0.8, hjust = -0.4,angle = -50, size = 3.5) +
    
    # Original True ER line for DH1
    geom_line(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH1"), size = 1.5) +
    geom_point(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], color = "True ER_DH1"), size = 2) +
    geom_text(data = TRUE_DH1, aes(x = .data[[x_var]], y = .data[[y_var]], label = DOSE), 
              vjust = 0.2, hjust = -0.4,angle = 75, size = 3.5) +
    
    custom_theme +
    theme(
      panel.background = element_rect(fill = "white", color = "black"),
      legend.background = element_rect(fill = "transparent"),
      legend.position = c(0.3, 0.8),
      legend.title = element_blank(),
      axis.text.x = element_text(size = 12, angle = 0, hjust = 1),
      axis.text.y = element_text(size = 12),
      axis.title = element_text(size = 12),
      plot.title = element_text(size = 14, hjust = 0.5),
      plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm")
        ) +
    labs(
      x = x_var,
      y = "Probability of ORR Event",
      title = paste("Logistic Regression -", x_var),
      color = "Model"
    ) +
   coord_cartesian(ylim = c(0, 1), xlim = c(0.1, NA))+
    scale_y_continuous(breaks = seq(0, 1, 0.2)) +
    scale_x_log10(labels = custom_log_labels) +
    scale_color_manual(values = c("Logistic Regression" = "black","True ER_DH2" = "blue", "True ER_DH1" = "forestgreen"))
}

## compare the true ER for DH1 and DH2
# Logiplot1 <- logistic_regression_comparison(logistic_Results_plot$avgDoseTE, True.ER, ORR_trueER_DH2, "avgDoseTE", "EVENT")
Logiplot2 <- logistic_regression_comparison(logistic_Results_plot$Ctrough1D, True.ER, ORR_trueER_DH2, "Ctrough1D", "EVENT")
Logiplot3 <- logistic_regression_comparison(logistic_Results_plot$Cavg1D, True.ER, ORR_trueER_DH2, "Cavg1D", "EVENT")
Logiplot4 <- logistic_regression_comparison(logistic_Results_plot$CtroughOED, True.ER, ORR_trueER_DH2, "CtroughOED", "EVENT")
Logiplot5 <- logistic_regression_comparison(logistic_Results_plot$CavgOED, True.ER, ORR_trueER_DH2, "CavgOED", "EVENT")
Logiplot6 <- logistic_regression_comparison(logistic_Results_plot$Cavg1WOED, True.ER, ORR_trueER_DH2, "Cavg1WOED", "EVENT")
# Logiplot7 <- logistic_regression_comparison(logistic_Results_plot$Cavg2WOED, True.ER, ORR_trueER_DH2, "Cavg2WOED", "EVENT")
Logiplot8 <- logistic_regression_comparison(logistic_Results_plot$CavgTE, True.ER, ORR_trueER_DH2, "CavgTE", "EVENT")

Logistic_comparison <- grid.arrange(Logiplot2, Logiplot4, Logiplot6, Logiplot3, Logiplot5, Logiplot8,ncol = 3)

ggsave("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/True ER comparions_DH1&2_ORR_logtransform.tiff",
      plot = Logistic_comparison, 
     width = 15, height = 8, dpi = 400, units = "in")
```
## Select model_Observed vs. Predicted_5 quantiles
```{r}
quantiles_Five <- function(data, column_name, labels = c("1", "2", "3", "4", "5")) {
  quantiles <- quantile(data[[column_name]], probs = seq(0.2, 0.8, by = 0.2))
  categorized_column <- cut(data[[column_name]],
                            breaks = c(-Inf, quantiles, Inf),
                            labels = labels,
                            include.lowest = TRUE)
  return(categorized_column)
}

my.theme = theme_bw() +
  theme(plot.background  = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text      = element_text(size = 7),
        legend.title     = element_text(size = 7),
        axis.title       = element_text(size = 18),
        axis.text        = element_text(size = 12),
        legend.key.width = unit(.5,"cm"))

create_covariate_plot <- function(covariate_name) {
  # Read data
  setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR")
  file_path <- "logistic_regression_results.xlsx"
  Prediction <- read_excel(file_path, sheet = covariate_name)
  
  setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR")
  file_path <- "logistic_regression_results_test.xlsx"
  Prediction_log <- read_excel(file_path, sheet = covariate_name)
  
  # Calculate statistics
  covariate_stats <- quantile(df.ER.IDQ[[covariate_name]], probs = c(0.05, 0.5, 0.95), na.rm = TRUE)
  names(covariate_stats) <- c("p05", "med", "p95")
  
  # Prepare plot data
  eff.stats <- df.ER.IDQ %>%
    group_by(!!sym(paste0(covariate_name, "_IDQ"))) %>%
    summarise(N = n(),
              NResp = sum(EVENT == 1),
              Minimum = min(!!sym(covariate_name)),
              Median = median(!!sym(covariate_name)),
              Maximum = max(!!sym(covariate_name)),
              ObsProb = round(NResp / N, 4)) %>%
    mutate(bins = paste0(row_number(), "^", c("st", "nd", "rd", rep("th", n() - 3)), "^ quartile")) %>%
    select(bins, N, Minimum, Median, Maximum, NResp, ObsProb) %>%
    group_by(bins) %>%
    mutate(exact.lower = binom.test(NResp, N)$conf.int[1],
           exact.upper = binom.test(NResp, N)$conf.int[2]) %>%
    as.data.frame()
  
  # Create plot
   p <- ggplot() +
    geom_jitter(data = df.ER.IDQ, aes(x = !!sym(covariate_name), y = EVENT, color = "Observation"), alpha = 0.2, size = 1, height = 0.03) +
    
       # Original True ER line for DH2
    geom_line(data = TRUE_DH2, aes(x = !!sym(covariate_name), y =  EVENT, color = "True ER_DH2"), size = 1.5) +
    geom_point(data = TRUE_DH2, aes(x = !!sym(covariate_name), y =  EVENT, color = "True ER_DH2"), size = 2) +
    geom_text(data = TRUE_DH2, aes(x = !!sym(covariate_name), y =  EVENT, label = DOSE, color = "True ER_DH2"), 
              vjust = 0.8, hjust = -0.4,angle = -50, size = 3.5) +
    
    # Original True ER line for DH1
    geom_line(data = TRUE_DH1, aes(x = !!sym(covariate_name), y =  EVENT, color = "True ER_DH1"), size = 1.5) +
    geom_point(data = TRUE_DH1, aes(x = !!sym(covariate_name), y =  EVENT, color = "True ER_DH1"), size = 2) +
    geom_text(data = TRUE_DH1, aes(x = !!sym(covariate_name), y =  EVENT, label = DOSE), 
              vjust = 0.2, hjust = -0.4,angle = 75, size = 3.5) +
    
    
    geom_line(data = Prediction, aes(x = Covariate, y = Predicted_Prob, color = "No log transformation"), size = 1.5) +
    geom_ribbon(data = Prediction, aes(x = Covariate, ymin = Lower_Bound, ymax = Upper_Bound), alpha = 0.2, fill = "#00BFC4") +
    
    
    geom_line(data = Prediction_log, aes(x = Covariate, y = Predicted_Prob, color = "Log transformation"), size = 1.5) +
    geom_ribbon(data = Prediction_log, aes(x = Covariate, ymin = Lower_Bound, ymax = Upper_Bound), alpha = 0.2, fill = "#F8766D") +
    
    geom_errorbar(data = eff.stats, aes(x = Median, ymin = exact.lower, ymax = exact.upper), size = 1.1, width = 0.1) +
    geom_point(data = eff.stats, aes(x = Median, y = ObsProb), size = 2) +
    geom_segment(aes(x = min(eff.stats$Minimum), xend = max(eff.stats$Maximum), y = -0.05, yend = -0.05), size = 1.1) +
    geom_segment(data = eff.stats, aes(x = Minimum, xend = Minimum, y = -0.07, yend = -0.03), size = 1.1) +
    geom_segment(data = eff.stats[nrow(eff.stats), ], aes(x = Maximum, xend = Maximum, y = -0.07, yend = -0.03), size = 1.1) +
    geom_vline(xintercept = covariate_stats["med"], linetype = 'solid') +
    geom_vline(xintercept = covariate_stats["p05"], linetype = 'dashed') +
    geom_vline(xintercept = covariate_stats["p95"], linetype = 'dashed') +
    scale_color_manual(values = c("Observation" = "black", "No log transformation" = "#00BFC4", "Log transformation" = "#F8766D","True ER_DH2" = "blue", "True ER_DH1" = "forestgreen")) +
    my.theme +
    xlab(covariate_name) + 
    ylab("Probability of Responder") +
    ggtitle(paste("Model comparison: log vs no log -", covariate_name)) +
    theme(
      legend.position = c(0.7, 0.3),
      legend.background = element_rect(fill = "transparent"),
      legend.title = element_blank(),
      legend.text = element_text(size = 9),
      legend.key.size = unit(0.5, "cm"),
      axis.text.x = element_text(size = 12, angle = 0, hjust = 1),
      axis.text.y = element_text(size = 12),
      axis.title = element_text(size = 12),
      plot.title = element_text(size = 14, hjust = 0.5),
      plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm")
    )
  
  return(p)
}

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR")
df.ER.IDQ <- read.csv("df_ER_IDQ.csv")

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/True ER relationship/DH1")
TRUE_DH1 <- read.csv("True ER_ORR.csv")

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/True ER relationship/DH2_LDR_method3")
TRUE_DH2 <- read.csv("True ER_ORR_LDR_DH2.csv")

df.ER.IDQ$Ctrough1D_IDQ  <- quantiles_Five(df.ER.IDQ, "Ctrough1D")
df.ER.IDQ$CtroughOED_IDQ  <- quantiles_Five(df.ER.IDQ, "CtroughOED")
df.ER.IDQ$Cavg1D_IDQ  <- quantiles_Five(df.ER.IDQ, "Cavg1D")
df.ER.IDQ$CavgOED_IDQ  <- quantiles_Five(df.ER.IDQ, "CavgOED")
df.ER.IDQ$Cavg1WOED_IDQ  <- quantiles_Five(df.ER.IDQ, "Cavg1WOED")
df.ER.IDQ$Cavg2WOED_IDQ  <- quantiles_Five(df.ER.IDQ, "Cavg2WOED")
df.ER.IDQ$CavgTE_IDQ  <- quantiles_Five(df.ER.IDQ, "CavgTE")

plot_Ctrough1D <- create_covariate_plot("Ctrough1D")
plot_Cavg1D <- create_covariate_plot("Cavg1D")
plot_Cavg1WOED <- create_covariate_plot("Cavg1WOED")
plot_CtroughOED <- create_covariate_plot("CtroughOED")
plot_CavgOED <- create_covariate_plot("CavgOED")
plot_CavgTE <- create_covariate_plot("CavgTE")

plot_Ctrough1D_L <- create_covariate_plot("Ctrough1D")+ scale_x_log10(labels = custom_log_labels) + coord_cartesian(ylim = c(0, 1), xlim = c(1, NA))+ theme(legend.position = c(0.3, 0.7))
plot_Cavg1D_L <- create_covariate_plot("Cavg1D")+ scale_x_log10(labels = custom_log_labels) + coord_cartesian(ylim = c(0, 1), xlim = c(1, NA))+ theme(legend.position = c(0.3, 0.7))
plot_Cavg1WOED_L <- create_covariate_plot("Cavg1WOED")+ scale_x_log10(labels = custom_log_labels) + coord_cartesian(ylim = c(0, 1), xlim = c(1, NA))+ theme(legend.position = c(0.3, 0.7))
plot_CtroughOED_L <- create_covariate_plot("CtroughOED")+ scale_x_log10(labels = custom_log_labels) + coord_cartesian(ylim = c(0, 1), xlim = c(1, NA))+ theme(legend.position = c(0.3, 0.7))
plot_CavgOED_L <- create_covariate_plot("CavgOED")+ scale_x_log10(labels = custom_log_labels) + coord_cartesian(ylim = c(0, 1), xlim = c(1, NA))+ theme(legend.position = c(0.3, 0.7))
plot_CavgTE_L <- create_covariate_plot("CavgTE")+ scale_x_log10(labels = custom_log_labels) + coord_cartesian(ylim = c(0, 1), xlim = c(1, NA))+ theme(legend.position = c(0.3, 0.7))

model_comparison <- grid.arrange(plot_Ctrough1D, plot_Cavg1D, plot_Cavg1WOED, plot_CtroughOED,plot_CavgOED,plot_CavgTE,ncol = 3)
ggsave("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/model comparision results_linear_5.tiff",
      plot = model_comparison, 
     width = 15, height = 8, dpi = 400, units = "in")

model_comparison_L <- grid.arrange(plot_Ctrough1D_L, plot_Cavg1D_L, plot_Cavg1WOED_L, plot_CtroughOED_L,plot_CavgOED_L,plot_CavgTE_L,ncol = 3)
ggsave("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR/model comparision results_log_5.tiff",
      plot = model_comparison_L, 
     width = 15, height = 8, dpi = 400, units = "in")

```

* Vertical dashed lines are the 5^th^ and 95^th^ percentiles for observed average concentrations.
* Vertical solid line is the median observed average concentration.
* Cave quartiles are plotted along the x-axis.
* Error bars are plotted at the median of the Cave quartiles.
* The upper red dots and line are the probability of being a responder for a typical subject.
* The lower red dots and line are the probability of being a responder for a typical subject.

#6 model comparision
```{r}
setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR")
df.ER.IDQ <- read.csv("df_ER_IDQ.csv")

covariates <- c( "Ctrough1D", "Cavg1D","CtroughOED", "CavgOED", "Cavg1WOED","CavgTE")

logistic_formulas <- sapply(covariates, function(x) as.formula(paste('EVENT ~', x)))
logistic_Results <- lapply(logistic_formulas, function(x) glm(x, family = binomial(logit), data = df.ER.IDQ))
logistic_result  <- logistic_analysis(logistic_Results,covariates)%>% 
                    rownames_to_column(var = "Variable")


logistic_formulas_log <- sapply(covariates, function(x) as.formula(paste('EVENT ~ log(', x, ')')))
logistic_Results_log <- lapply(logistic_formulas_log, function(x) glm(x, family = binomial(logit), data = df.ER.IDQ))
logistic_result_log  <- logistic_analysis(logistic_Results_log,covariates)%>% 
                    rownames_to_column(var = "Variable")

wb_model <- createWorkbook()
addWorksheet(wb_model, "log transform")
addWorksheet(wb_model, "no log transform")


writeData(wb_model, sheet = "log transform", x = logistic_result_log)
writeData(wb_model, sheet = "no log transform", x = logistic_result)

setwd("C:/Users/Xuefen.Yin/OneDrive - FDA/ER2 analysis/ORR_2D_include PFS truncation/True Positive ER_ORR_DH2_HL24_ID20871_ii24_200&100_LDR")
saveWorkbook(wb_model, file = "model comparison_ORR.xlsx", overwrite = TRUE)
```

